---
title: "Untitled"
output: html_document
---
#I. Survival Analysis Basics

http://www.sthda.com/english/wiki/survival-analysis-basics

Survival analysis is used in a variety of field such as:

Cancer studies for patients survival time analyses,
Sociology for “event-history analysis”,
and in engineering for “failure-time analysis”.
In cancer studies, typical research questions are like:

What is the impact of certain clinical characteristics on patient’s survival
What is the probability that an individual survives 3 years?
Are there differences in survival between groups of patients?
```{r}
library("survival")
library("survminer")
```


```{r}
data("lung")
head(lung)
```
inst: Institution code
time: Survival time in days
status: censoring status 1=censored, 2=dead
age: Age in years
sex: Male=1 Female=2
ph.ecog: ECOG performance score (0=good 5=dead)
ph.karno: Karnofsky performance score (bad=0-good=100) rated by physician
pat.karno: Karnofsky performance score as rated by patient
meal.cal: Calories consumed at meals
wt.loss: Weight loss in last six months
## Compute survival curves: survfit()
We want to compute the survival probability by sex.

The function survfit() [in survival package] can be used to compute kaplan-Meier survival estimate. Its main arguments include:

a survival object created using the function Surv()
and the data set containing the variables.
To compute survival curves, type this:
```{r}
fit <- survfit(Surv(time, status) ~ sex, data = lung)
print(fit)
```
By default, the function print() shows a short summary of the survival curves. It prints the number of observations, number of events, the median survival and the confidence limits for the median.

```{r}
table(lung$status)
# 165 death, 63 censor
# in 165 death: 112 man, 53 woman
```


```{r}
library(tidyverse)
lung %>% 
  group_by(sex) %>% 
  #select(sex,status) %>% 
  filter(status == 2) %>% 
  count(status)
```


```{r}
# Summary of survival curves
#summary(fit)
# Access to the sort summary table
summary(fit)$table
```
```{r}
library(broom)
tidy(fit)
```
n: total number of subjects in each curve.
time: the time points on the curve.
n.risk: the number of subjects at risk at time t
n.event: the number of events that occurred at time t.
n.censor: the number of censored subjects, who exit the risk set, without an event, at time t.
lower,upper: lower and upper confidence limits for the curve, respectively.
strata: indicates stratification of curve estimation. If strata is not NULL, there are multiple curves in the result. The levels of strata (a factor) are the labels for the curves.

```{r}
d <- data.frame(time = fit$time,
                  n.risk = fit$n.risk,
                  n.event = fit$n.event,
                  n.censor = fit$n.censor,
                  surv = fit$surv,
                  upper = fit$upper,
                  lower = fit$lower
                  )
head(d)
```

## Visualize survival curves
We’ll use the function ggsurvplot() [in Survminer R package] to produce the survival curves for the two groups of subjects.

It’s also possible to show:

the 95% confidence limits of the survivor function using the argument conf.int = TRUE.
the number and/or the percentage of individuals at risk by time using the option risk.table. Allowed values for risk.table include:
TRUE or FALSE specifying whether to show or not the risk table. Default is FALSE.
“absolute” or “percentage”: to show the absolute number and the percentage of subjects at risk by time, respectively. Use “abs_pct” to show both absolute number and percentage.
the p-value of the Log-Rank test comparing the groups using pval = TRUE.
horizontal/vertical line at median survival using the argument surv.median.line. Allowed values include one of c(“none”, “hv”, “h”, “v”). v: vertical, h:horizontal.
```{r}
# Change color, linetype by strata, risk.table color by strata
ggsurvplot(fit,
          pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF"))

```
The plot can be further customized using the following arguments:

conf.int.style = “step” to change the style of confidence interval bands.
xlab to change the x axis label.
break.time.by = 200 break x axis in time intervals by 200.
risk.table = “abs_pct”to show both absolute number and percentage of individuals at risk.
risk.table.y.text.col = TRUE and risk.table.y.text = FALSE to provide bars instead of names in text annotations of the legend of risk table.
ncensor.plot = TRUE to plot the number of censored subjects at time t. As suggested by Marcin Kosinski, This is a good additional feedback to survival curves, so that one could realize: how do survival curves look like, what is the number of risk set AND what is the cause that the risk set become smaller: is it caused by events or by censored events?
legend.labs to change the legend labels.

```{r}
ggsurvplot(
   fit,                     # survfit object with calculated statistics.
   pval = TRUE,             # show p-value of log-rank test.
   conf.int = TRUE,         # show confidence intervals for 
                            # point estimaes of survival curves.
   conf.int.style = "step",  # customize style of confidence intervals
   xlab = "Time in days",   # customize X axis label.
   break.time.by = 200,     # break X axis in time intervals by 200.
   ggtheme = theme_light(), # customize plot and risk table with a theme.
   risk.table = "abs_pct",  # absolute number and percentage at risk.
  risk.table.y.text.col = T,# colour risk table text annotations.
  risk.table.y.text = FALSE,# show bars instead of names in text annotations
                            # in legend of risk table.
  ncensor.plot = TRUE,      # plot the number of censored subjects at time t
  surv.median.line = "hv",  # add the median survival pointer.
  legend.labs = 
    c("Male", "Female"),    # change legend labels.
  palette = 
    c("#E7B800", "#2E9FDF") # custom color palettes.
)
```
The Kaplan-Meier plot can be interpreted as follow:


The horizontal axis (x-axis) represents time in days, and the vertical axis (y-axis) shows the probability of surviving or the proportion of people surviving. The lines represent survival curves of the two groups. A vertical drop in the curves indicates an event. The vertical tick mark on the curves means that a patient was censored at this time.

At time zero, the survival probability is 1.0 (or 100% of the participants are alive).
At time 250, the probability of survival is approximately 0.55 (or 55%) for sex=1 and 0.75 (or 75%) for sex=2.
The median survival is approximately 270 days for sex=1 and 426 days for sex=2, suggesting a good survival for sex=2 compared to sex=1


The median survival times for each group can be obtained using the code below:

```{r}
summary(fit)$table
```
The median survival times for each group represent the time at which the survival probability, S(t), is 0.5.

The median survival time for sex=1 (Male group) is 270 days, as opposed to 426 days for sex=2 (Female). There appears to be a survival advantage for female with lung cancer compare to male. However, to evaluate whether this difference is statistically significant requires a formal statistical test, a subject that is discussed in the next sections.

Note that, the confidence limits are wide at the tail of the curves, making meaningful interpretations difficult. This can be explained by the fact that, in practice, there are usually patients who are lost to follow-up or alive at the end of follow-up. Thus, it may be sensible to shorten plots before the end of follow-up on the x-axis (Pocock et al, 2002).

The survival curves can be shorten using the argument xlim as follow:
```{r}
ggsurvplot(fit,
          conf.int = TRUE,
          risk.table.col = "strata", # Change risk table color by groups
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF"),
          xlim = c(0, 600))
```
Note that, three often used transformations can be specified using the argument fun:

“log”: log transformation of the survivor function,
“event”: plots cumulative events (f(y) = 1-y). It’s also known as the cumulative incidence,
“cumhaz” plots the cumulative hazard function (f(y) = -log(y))


For example, to plot cumulative events, type this:

```{r}
ggsurvplot(fit,
          conf.int = TRUE,
          risk.table.col = "strata", # Change risk table color by groups
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF"),
          fun = "event")
```
```{r}
ggsurvplot(fit,
          conf.int = TRUE,
          risk.table.col = "strata", # Change risk table color by groups
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF"),
          fun = "cumhaz")
```


```{r}
summary(fit)
```


```{r}
res.sum <- surv_summary(fit)
head(res.sum)
```
The function surv_summary() returns a data frame with the following columns:

time: the time points at which the curve has a step.
n.risk: the number of subjects at risk at t.
n.event: the number of events that occur at time t.
n.censor: number of censored events.
surv: estimate of survival probability.
std.err: standard error of survival.
upper: upper end of confidence interval
lower: lower end of confidence interval
strata: indicates stratification of curve estimation. The levels of strata (a factor) are the labels for the curves.

```{r}
attr(res.sum, "table")
```


```{r}
surv_diff <- survdiff(Surv(time, status) ~ sex, data = lung)
surv_diff
```
The log rank test for difference in survival gives a p-value of p = 0.0013, indicating that the sex groups differ significantly in survival.

## Fit complex survival curves
```{r}
require("survival")
fit2 <- survfit( Surv(time, status) ~ sex + rx + adhere,
                data = colon )
```

```{r}
# Plot survival curves by sex and facet by rx and adhere
ggsurv <- ggsurvplot(fit2, fun = "event", conf.int = TRUE,
                     ggtheme = theme_bw())
   
ggsurv$plot +theme_bw() + 
  theme (legend.position = "right")+
  facet_grid(rx ~ adhere)
```

https://www.rdocumentation.org/packages/sampling/versions/2.8/topics/strata
```{r}
## Example 1
############
# Example from An and Watts (New SAS procedures for Analysis of Sample Survey Data)
# generates artificial data (a 235X3 matrix with 3 columns: state, region, income).
# the variable "state" has 2 categories ('nc' and 'sc'). 
# the variable "region" has 3 categories (1, 2 and 3).
# the sampling frame is stratified by region within state.
# the income variable is randomly generated
data=rbind(matrix(rep("nc",165),165,1,byrow=TRUE),matrix(rep("sc",70),70,1,byrow=TRUE))
data=cbind.data.frame(data,c(rep(1,100), rep(2,50), rep(3,15), rep(1,30),rep(2,40)),
1000*runif(235))
names(data)=c("state","region","income")
# computes the population stratum sizes
data

```


```{r}
table(data$region,data$state)
```


```{r}
# there are 5 cells with non-zero values
# one draws 5 samples (1 sample in each stratum)
# the sample stratum sizes are 10,5,10,4,6, respectively
# the method is 'srswor' (equal probability, without replacement)
s=strata(data,c("region","state"),size=c(10,5,10,4,6), method="srswor")
getdata(data,s)
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

