---
title: "Credit_card"
output: html_document
---

The datasets contains transactions made by credit cards in September 2013 by european cardholders.
This dataset presents transactions that occurred in two days, where we have 492 frauds out of 284,807 transactions. The dataset is highly unbalanced, the positive class (frauds) account for 0.172% of all transactions.

It contains only numerical input variables which are the result of a PCA transformation. Unfortunately, due to confidentiality issues, we cannot provide the original features and more background information about the data. Features V1, V2, … V28 are the principal components obtained with PCA, the only features which have not been transformed with PCA are 'Time' and 'Amount'. Feature 'Time' contains the seconds elapsed between each transaction and the first transaction in the dataset. The feature 'Amount' is the transaction Amount, this feature can be used for example-dependant cost-senstive learning. Feature 'Class' is the response variable and it takes value 1 in case of fraud and 0 otherwise.
```{r}
library(tidyverse)
library(data.table)
library(caret)
library(recipes) # create preprocess ml pipeline
```

```{r}
getwd()
```

```{r}
#path='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_4000_tail.dat'
path="/media/ad/01D6B57CFBE4DB20/1.Linux/Data/creditcard.csv"
data <- fread(path)
data
```
# Check null value

```{r}
sum(is.na(data))
```
No null value in this dataset

```{r}
library(base)
base::table(data$Class)
```


```{r}
library(DataExplorer)
```


```{r}
## View basic description for airquality data
introduce(data)
```


```{r}
## Plot basic description for airquality data
plot_intro(data)
```

```{r}
## View missing value distribution for airquality data
plot_missing(data)
```


```{r}
## Left: frequency distribution of all discrete variables
plot_bar(data)
```


```{r}
## View histogram of all continuous variables
plot_histogram(data)
```


```{r}
## View estimated density distribution of all continuous variables
plot_density(data)
```


```{r}
## View quantile-quantile plot of all continuous variables
#plot_qq(data)
```

```{r}
corr_matrix <- cor(data %>% select_if(is.numeric))
corr_matrix <- round(corr_matrix,2)
class(corr_matrix)
corr_matrix_df <- as.data.frame(apply(corr_matrix, 2, unlist)) %>% select(Class) %>% arrange(desc(Class))
# Name the unnamed first column
corr_matrix_df <- cbind(Features= rownames(corr_matrix_df), corr_matrix_df)
rownames(corr_matrix_df) <- NULL
corr_matrix_df
```
```{r}
# Top 10 for correlation
top_10 <-corr_matrix_df[1:11,1]
top_20 <-corr_matrix_df[1:21,1]
class(top_20)
top_20
```
```{r}
## View overall correlation heatmap
plot_correlation(data)
```

```{r}
library(dlookr)
plot_correlate(data)
```

```{r}
Categorical_vs_quantitative_plot <- function(data,categorical_col,quantitative_col){
  # plot the distribution using violin and boxplots
  ggplot(data, aes_(x = categorical_col, 
                     y = quantitative_col)) +
  geom_violin(fill = "cornflowerblue") +
  geom_boxplot(width = .2, 
               fill = "orange",
               outlier.color = "orange",
               outlier.size = 2) 
}
```

```{r}
corr_matrix_df
```


```{r}
Categorical_vs_quantitative_plot(data,~factor(Class),~V11)
Categorical_vs_quantitative_plot(data,~factor(Class),~V4)
Categorical_vs_quantitative_plot(data,~factor(Class),~V2)
Categorical_vs_quantitative_plot(data,~factor(Class),~V12)
Categorical_vs_quantitative_plot(data,~factor(Class),~V14)
Categorical_vs_quantitative_plot(data,~factor(Class),~V17)
```

# Machine learning model
## Prepare data for machine learning
```{r}
library(tidyverse)
library(data.table)
library(caret)
library(recipes) # create preprocess ml pipeline
```


```{r}
#path='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_4000_tail.dat'
path="/media/ad/01D6B57CFBE4DB20/1.Linux/Data/creditcard.csv"
data <- fread(path)
```

```{r}
# all character columns to factor:
data <- mutate_if(data, is.character, as.factor)
data$Class <-as.factor(data$Class)
#data$Attrition<-ifelse(data$Attrition=="Yes", 1, 0)
# Create training (80%) and test (20%) sets for the 
set.seed(430)
split = createDataPartition(data$Class, p =0.8, list = FALSE)
train = data[split, ]
test = data[-split, ]
dim(train)
dim(test)
```

While your project’s needs may vary, here is a suggested order of potential steps that should work for most problems:

Filter out zero or near-zero variance features.
Perform imputation if required.
Normalize to resolve numeric feature skewness.
Standardize (center and scale) numeric features.

```{r}
blueprint <- recipe(Class ~ ., data = train) %>%
  step_nzv(all_nominal(),-all_outcomes())  %>% 
  #step_knnimpute(all_predictors(), neighbors = 6) %>%  # Impute, very slow in large data in train, need step outside
  step_YeoJohnson(all_numeric(),-all_outcomes()) %>% # Remove skewness
  step_center(all_numeric(), -all_outcomes()) %>% # center 
  step_scale(all_numeric(), -all_outcomes()) #%>% # scale
  #step_dummy(all_nominal(), one_hot = TRUE) %>% 
  #step_pca(all_numeric(), -all_outcomes()) #Perform dimension reduction
blueprint
```
Next, we need to train this blueprint on some training data. Remember, there are many feature engineering steps that we do not want to train on the test data (e.g., standardize and PCA) as this would create data leakage. So in this step we estimate these parameters based on the training data of interest.

```{r}
prepare <- prep(blueprint, training = train)
prepare
```
Lastly, we can apply our blueprint to new data (e.g., the training data or future test data) with bake()

```{r}
baked_train <- bake(prepare, new_data = train)
baked_test <- bake(prepare, new_data = test)
head(baked_train)
```
6. Check mulity caret ML model

```{r}
#library(caret) # logistic regression, lm, knn, 
#library(glmnet)   # for implementing regularized regression
#library(earth)     # for fitting MARS models
#library(rpart) # decision tree
#library(ipred)       # for fitting bagged decision trees
#library(ranger)   # a c++ implementation of random forest 

library(doParallel)
cl <-makePSOCKcluster(5)
registerDoParallel(cl)
```
```{r}
list_model <- c("knn","rpart","lda","svmRadial","ranger","LogitBoost","naive_bayes","gbm","gbm_h2o","glmnet_h2o")
```

6 GB for 100 MB data train by lda, very long
4 GB for gbm model
```{r}
metric <- "Accuracy"
model_name <- "gbm" # Stochastic Gradient Boosting
start_time <- lubridate::second(Sys.time())
model <- train(Class~., data=baked_train, 
               method=model_name, metric=metric)
end_time <- lubridate::second(Sys.time())
time <- (end_time - start_time)
print(time)
```


```{r}
metric <- "Accuracy"
model_name <- "mlpSGD" # Multilayer Perceptron Network by Stochastic Gradient Descent
start_time <- lubridate::second(Sys.time())
model <- train(Class~., data=baked_train, 
               method=model_name, metric=metric)
end_time <- lubridate::second(Sys.time())
time <- (end_time - start_time)
print(time)
```

# H2O machine learning model
```{r}
library(h2o)
h2o.no_progress()
h2o.init()
```


```{r}
# convert training data to h2o object
train_h2o <- as.h2o(baked_train)
test_h2o <- as.h2o(baked_test)
# set the response column to Sale_Price
response <- "Class"
n_features <- length(setdiff(names(baked_train), "Class"))
# set the predictor names
predictors <- setdiff(colnames(baked_train), response)
```

XGboost H2O
```{r}
start_time <- Sys.time()
h2o_model <- h2o.xgboost(
    x = predictors, 
    y = response,
    training_frame = train_h2o, 
    seed = 123
)
end_time <- Sys.time()
h2o_model
pred <-h2o.predict(h2o_model, newdata = test_h2o)
time <- (end_time - start_time)
print(time) # 57 s mcc 0.84

```


```{r}
h2o.performance(h2o_model, newdata = test_h2o) # mcc 0.84
```

Gradient Boosting Machine (GBM)

```{r}
n_features
```

```{r}
start_time <- Sys.time()
h2o_gbm <- h2o.gbm(
    x = predictors, 
    y = response,
    training_frame = train_h2o, 
    ntrees = n_features * 10, # very slow if high dim, not pca
    #learn_rate=0.2,
    seed = 123
)
end_time <- Sys.time()
h2o_gbm
pred <-h2o.predict(h2o_gbm, newdata = test_h2o)
time <- (end_time - start_time)
print(time) # 1.79 mins mcc: 0.48 (gan voi f1)
```


```{r}
h2o.performance(h2o_gbm, newdata = test_h2o) # mcc: 0.48 (gan voi f1)
```
Generalized Linear Models (GLM)

```{r}
start_time <- Sys.time()
print(start_time)
h2o_glm <- h2o.glm(
    x = predictors, 
    y = response,
    training_frame = train_h2o, 
    #lambda_search = TRUE,
    seed = 123
)
end_time <- Sys.time()
print(end_time)
h2o_glm
pred <-h2o.predict(h2o_glm, newdata = test_h2o)
time <- (end_time - start_time)
print(time) # 3.79 s mcc 0.755
```

```{r}
h2o.performance(h2o_glm, newdata = test_h2o) # mcc 0.755
```

Random forest
```{r}
start_time <- Sys.time()
print(start_time)
h2o_rf1 <- h2o.randomForest(
    x = predictors, 
    y = response,
    training_frame = train_h2o, 
    ntrees = n_features * 10, # very slow if high dim, not pca
    #ntrees=300,
    seed = 123
)
end_time <- Sys.time()
print(end_time)
h2o_rf1
pred <-h2o.predict(h2o_rf1, newdata = test_h2o)
time <- (end_time - start_time)
print(time) # 2.1 mins mcc 0.87
```

```{r}
h2o.performance(h2o_rf1, newdata = test_h2o)
```

```{r}
a <- Sys.time()
b <- Sys.time()
b-a
lubridate::second(Sys.time())
lubridate::minute(Sys.time())
```

# Explain model
```{r}
perf <- h2o.performance(h2o_model, newdata = test_h2o)
plot(perf, type = "roc")
```

```{r}
h2o.varimp_plot(h2o_model)
```

```{r}
#class(test_h2o$Class)
test_h2o$Class
```

```{r}
class(pred$predict)
pred$predict
```
```{r}
levels(test_h2o$Class)
levels(pred$predict)
```
```{r}
as.data.frame(test_h2o$Class)
```
```{r}
print("pred")
as.factor(as.data.frame(pred$predict))
print("test")
as.factor(as.data.frame(test_h2o$Class))
```


```{r}
confusionMatrix(as.factor(as.data.frame(pred$predict)), as.factor(as.data.frame(test_h2o$Class)))
```


```{r}
confusionMatrix(pred$predict, as.factor(test_h2o$Class))
```

```{r}
```


```{r}
```

