---
title: "Untitled"
output: html_document
---
# Get data
```{r}
#install.packages("tidymodels")
library(modeldata)
library(tidymodels)
data(ames)
ames
```

# Split data
```{r}
ames <- ames %>% mutate(Sale_Price = log10(Sale_Price))

set.seed(123)
ames_split <- initial_split(ames, prob = 0.80, strata = Sale_Price)
ames_train <- training(ames_split)
ames_test  <-  testing(ames_split)
ames_train_select <- ames_train %>% select(Sale_Price, Neighborhood , Gr_Liv_Area , Year_Built , Bldg_Type , 
                Latitude , Longitude)
ames_train_select
```
```{r}
summary(ames_train_select)
```
# Recipe:

The call to recipe() with a formula tells the recipe the roles of the variables (e.g., predictor, outcome). It only uses the data to determine the data types for the columns.

step_log() declares that Gr_Liv_Area should be log transformed.

step_dummy() is used to specify which variables should be converted from a qualitative format to a quantitative format, in this case, using dummy or indicator variables. An indicator or dummy variable is a binary numeric variable (a column of ones and zeroes) that encodes qualitative information; we will dig deeper into these kinds of variables in Section 6.3.

The function all_nominal() captures the names of any columns that are currently factor or character (i.e., nominal) in nature. This is a dplyr selector function similar to starts_with() or matches() but can only be used inside of a recipe.

Other selectors specific to the recipes package are: all_numeric(), all_predictors(), and all_outcomes(). As with dplyr, one or more unquoted expressions, separated by commas, can be used to select which columns are affected by each step.
```{r}
ames_rec <- 
  recipe(Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built + Bldg_Type + 
           Latitude + Longitude, data = ames_train) %>%
  step_log(Gr_Liv_Area, base = 10) %>% # declares that Gr_Liv_Area should be log transformed.
  step_other(Neighborhood, threshold = 0.01) %>% #  the bottom 1% of the neighborhoods will be lumped into a new level called “other”
  step_dummy(all_nominal()) %>% 
  step_interact( ~ Gr_Liv_Area:starts_with("Bldg_Type_") ) %>% 
  step_ns(Latitude, Longitude, deg_free = 20) %>% 
  prep()

baked_train <- bake(ames_rec, new_data = ames_train)
baked_test <- bake(ames_rec, new_data = ames_test)
#str(baked_train)
```

# Fitting model with parsnip
```{r}
library(parsnip)
```

```{r}
linear_reg() %>% set_engine("glmnet") %>% translate()
```


```{r}
lm_model <- 
  linear_reg() %>% 
  set_engine("lm")
```


```{r}
lm_form_fit <- 
  lm_model %>% 
  # Recall that Sale_Price has been pre-logged
  fit(Sale_Price ~ Longitude + Latitude, data = ames_train)
lm_form_fit
```


```{r}
ames_test %>% 
  select(Sale_Price) %>% 
  bind_cols(predict(lm_form_fit, ames_test)) %>% 
  # Add 95% prediction intervals to the results:
  bind_cols(predict(lm_form_fit, ames_test, type = "pred_int")) 
```

# WORKFLOW BASICS

```{r}
lm_model <- linear_reg() %>% set_engine("lm")

lm_wflow <- 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(ames_rec)

lm_fit <- fit(lm_wflow, ames_train)
```


```{r}
predict(lm_fit, ames_test %>% slice(1:3))
```

# Judging model effectiveness

```{r}
ames_test_res <- predict(lm_fit, new_data = ames_test %>% select(-Sale_Price))
ames_test_res <- bind_cols(ames_test_res, ames_test %>% select(Sale_Price))
ames_test_res
```

```{r}
ames_metrics <- metric_set(rmse, rsq, mae)
ames_metrics(ames_test_res, truth = Sale_Price, estimate = .pred)
```
BINARY CLASSIFICATION METRICS

```{r}
data(two_class_example)
str(two_class_example)
```


```{r}
# A confusion matrix: 
yardstick::conf_mat(two_class_example, truth = truth, estimate = predicted)
yardstick::accuracy(two_class_example, truth = truth, estimate = predicted)
yardstick::mcc(two_class_example, truth, predicted)
yardstick::f_meas(two_class_example, truth, predicted)
```


```{r}
roc_auc(two_class_example, truth, Class1)
```


```{r}
two_class_curve <- roc_curve(two_class_example, truth, Class1)
autoplot(two_class_curve)
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

```{r}
```


```{r}
```

