---
title: "DJIA_30_stock"
output: html_document
---
```{r}
library(tidyverse)
library(data.table)
library(forecast)
```


```{r}
s_data <- read.csv(file ="data/all_stocks_2006-01-01_to_2018-01-01.csv")
s_data
```


```{r}
unique(s_data$Name)
length(unique(s_data$Name))
```

# 4 Data overview
```{r}
summary(s_data)
```


```{r}
str(s_data)
```

# 5 Data cleaning

```{r}
sum(is.na(s_data))
```


```{r}
library(lubridate)
s_data[is.na(s_data)] <- 0
s_data$Date <- ymd(s_data$Date)
str(s_data)
```

# Lets look at some univariate distributions - AllStocks Data
```{r}
#install.packages("pdp")
library(pdp)
```

```{r}
options(repr.plot.width=12, repr.plot.height=12) 

p1 = ggplot(s_data, aes(Open)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# + xlim(c(0, 1000))

p2 = ggplot(s_data, aes(High)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# + xlim(c(0, 1000))

p3 = ggplot(s_data, aes(Low)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# + xlim(c(0, 1000))

p4 = ggplot(s_data, aes(Close)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# + xlim(c(0, 1000))

pdp::grid.arrange(p1,p2,p3,p4, nrow=2,ncol=2)
```
```{r}
#tmp <- filter(s_data, High > 100)
tmp <- s_data
sample_num = 5
```


```{r}
#sample_ticker <- as.character(sample(tmp$Name, sample_num))
sample_ticker <"GOOGL"
candidate_ticker <- c("IBM", "BA", "AAPL", "GS", "GOOGL")
candidate_num <- length(candidate_ticker)
candidate_num # 5
stock_list <- vector(mode="list", length=candidate_num)
names(stock_list) <- candidate_ticker
stock_list
```


```{r}
i = 1
for (ticker in candidate_ticker){
  stock_list[[i]] <- filter(s_data, Name == ticker)
  # print(stock_list[[i]])
  i <- i+1
  # print(ticker)
}
```


```{r}
stock_list
```
# 8 Create and plot Time Series - High

```{r}
xts_list <- vector(mode="list", length=candidate_num)
ts_list <- vector(mode="list", length=candidate_num)
```


```{r}
names(xts_list) = candidate_ticker
names(ts_list) = candidate_ticker
xts_list
```


```{r}
library(xts)
for (ticker in candidate_ticker){
  stock = stock_list[[ticker]]
  xts = xts(stock$Close, order.by=stock$Date)
  attr(xts, 'frequency') <- length(xts)/12 # 251.5833 , time interval 12 years (all data)
  ts = as.ts(xts, start = c(2006))
  xts_list[[ticker]] <- xts
  ts_list[[ticker]] <- ts
}

```
```{r}
head(xts)
tail(xts)
```
```{r}
head(ts)
tail(ts)
```

```{r}
length(xts)
length(xts)/12
# frequency: 251 value each year, through 12 years
```


```{r}
xts_table= do.call(cbind, xts_list)
head(xts_table)
```


```{r}
#install.packages("dygraphs")
library(dygraphs)
dygraph(xts_table, xlab = "Time", ylab = "High value", main = "Time Series") %>%
  # dySeries(labels.default()) %>%
  # dyOptions(colors = c("red")) %>%
  dyRangeSelector()
```

# 9 Stationarity
```{r}
xts = xts_list[['GOOGL']]
ts = ts_list[['GOOGL']]
```

```{r}
head(xts)
```


```{r}
head(ts)
```


```{r}
library(tseries)
tseries::adf.test(xts, alternative = "stationary", k = 0)
```
# 10 Decomposing Time Series

```{r}
tscomponents_add <- decompose(ts, type = "additive")
tscomponents_mul <- decompose(ts, type = "multiplicative")
plot(tscomponents_add, col = "red")
```


```{r}
plot(tscomponents_mul, col = "blue")
```
# 11 Differencing a Time Series

Differencing is a common solution used to stationarize the variable. We will perform differencing using R function diff.

Consider fractional difference?
```{r}
xtsdiff1 <- diff(xts, differences=1)
tsdiff1 <- diff(ts, differences=1)
plot.xts(xtsdiff1, col = "blue")
```


```{r}
adf.test(tsdiff1, alternative = "stationary", k = 0)
```
Reject hypothesis --> stationary
It means that different make stationary

```{r}
findfrequency(xts)          # find dominant frequency of original time series
```


```{r}
findfrequency(xtsdiff1)     # find dominant frequency of differenced time series
```
The time series (above) appears to be stationary.

# 12 Selecting a Candidate ARIMA Model
The next step is to select appropriate ARIMA model, which means finding the most appropriate values of p and q for an ARIMA(p,d,q) model. You usually need to examine the correlogram and partial correlogram of the stationary time series for this. To plot a correlogram and partial correlogram, we can use the acf() and pacf() functions in R, respectively.


```{r}
Acf(xtsdiff1, lag.max=60)             # plot a correlogram
```


```{r}
Acf(xtsdiff1, lag.max=60, plot=FALSE) # get the autocorrelation values
```


```{r}
Pacf(xtsdiff1, lag.max=60)             # plot a partial correlogram
```


```{r}
Pacf(xtsdiff1, lag.max=60, plot=FALSE) # get the partial autocorrelation values
```
Now, we could compare the sample ACF and PACF to those of various theoretical ARMA models. Use properties of ACF & PACF as a guide to estimate plausible models and select appropriate p, q and d. Alternative to this is discussed next.

# 13 Fitting an ARIMA Model

R provides a function auto.arima, which returns best ARIMA model according to either AIC, AICc or BIC value. The function conducts a search over possible model within the order constraints provided.

We train 6 models with different training data. For example, the model ‘tsarima240’ is trained with the whole time series exluding the last 240 daily data.


```{r}
length(xts)
length(head(xts, -240))
```


```{r}
tsarima240 <- auto.arima(head(xts, -240), max.p = 3, max.q = 3, max.d = 3) # excluding last 240 time series as test data
print(tsarima240)
```


```{r}
autoplot(tsarima240)
```


```{r}
tsarima120 <- auto.arima(head(xts, -120), max.p = 3, max.q = 3, max.d = 3) #120
print(tsarima120)
```


```{r}
autoplot(tsarima120)
```


```{r}
tsarima60 <- auto.arima(head(xts, -60), max.p = 3, max.q = 3, max.d = 3) #60
print(tsarima60)
tsarima30 <- auto.arima(head(xts, -30), max.p = 3, max.q = 3, max.d = 3) #30
print(tsarima30)
tsarima7 <- auto.arima(head(xts, -7), max.p = 3, max.q = 3, max.d = 3)   #7
print(tsarima7)
```

# 14 Forecasting using an ARIMA Model

```{r}
tsforecasts240 <- forecast(tsarima240, h = 240) # forecast the next 240 time series
tsforecasts120 <- forecast(tsarima120, h = 120) # forecast the next 120 time series
tsforecasts60 <- forecast(tsarima60, h = 60) # forecast the next 60 time series
tsforecasts30 <- forecast(tsarima30, h = 30) # forecast the next 30 time series
tsforecasts7 <- forecast(tsarima7, h = 7) # forecast the next 7 time series
```


```{r}
autoplot(tsforecasts240)
```

```{r}
length(head(tail(xts, 240), 240))
accuracy(tsforecasts240, head(tail(xts, 240), 240))
```


```{r}
length(head(tail(xts, 240), 120))
accuracy(tsforecasts240, head(tail(xts, 240), 120))
accuracy(tsforecasts240, head(tail(xts, 240), 60))
accuracy(tsforecasts240, head(tail(xts, 240), 30))
accuracy(tsforecasts240, head(tail(xts, 240), 7))
```


```{r}
ggplot(data.frame(residuals = tsforecasts240$residuals), aes(residuals)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# make a histogram
```


```{r}
checkresiduals(tsforecasts240)
```
# 15 Test arima_modeling function on the rest companies
```{r}
arima_modeling <- function(xts, ts, ticker){
  ## Stationarity
  print(ticker)
  adf.test(xts, alternative = "stationary", k = 0)

  ## Decomposing Time Series
  tscomponents <- decompose(ts)
  plot(tscomponents, col = "red")

  ## Differencing a Time Series
  xtsdiff1 <- diff(xts, differences=1)
  tsdiff1 <- diff(ts, differences=1)
  plot.xts(xtsdiff1, col = "blue")
  findfrequency(xts)          # find dominant frequency of original time series
  findfrequency(xtsdiff1)     # find dominant frequency of differenced time series

  ## Selecting a Candidate ARIMA Model
  print(ticker)
  print("Selecting a candidate ARIMA Model")
  Acf(xtsdiff1, lag.max=60)             # plot a correlogram
  Acf(xtsdiff1, lag.max=60, plot=FALSE) # get the autocorrelation values

  Pacf(xtsdiff1, lag.max=60)             # plot a partial correlogram
  Pacf(xtsdiff1, lag.max=60, plot=FALSE) # get the partial autocorrelation values
  
  ## Fitting an ARIMA Model
  tsarima <- auto.arima(head(xts, -30), max.p = 3, max.q = 3, max.d = 3)
  
  # excluding last 120 time series as test data
  print(tsarima)
  autoplot(tsarima)
  print(ticker)

  ## Forecasting using an ARIMA Model
  print(ticker)
  tsforecasts <- forecast(tsarima, h = 30) # forecast the next 120 time series
  acc <- accuracy(tsforecasts, head(tail(xts, 30), 7))
  print(acc)
  autoplot(tsforecasts)
  
  print(ticker)
  
  ggplot(data.frame(residuals = tsforecasts$residuals), aes(residuals)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# make a histogram
  checkresiduals(tsforecasts)
}

for (ticker in candidate_ticker){
  if (ticker != 'GOOGL'){
    arima_modeling(xts_list[[ticker]], ts_list[[ticker]], as.character(ticker))
    }
}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

