---
title: "Untitled"
output: html_document
---
# 1. Get data
```{r}
library(tidyverse)# include dplyr, tidr, ggplot2, tibble, readr, purr
library(recipes)
library(data.table)
library(rsample)   # for data splitting
library(caret)     # for model packages
```


```{r}
path="house_price_train.csv"
data <- fread(path)
dim(data)
head(data)
```
#2. Preprocess data
## Remove column with high null value (>50%)
```{r}
null_value <- sapply(data, function(x) sum(is.na(x)))
class(null_value)
null_value_df <- as.data.frame(null_value) %>% arrange(desc(null_value)) %>% filter(null_value > 0)
# Name the unnamed first column
null_value_df <- cbind(Features= rownames(null_value_df), null_value_df)
rownames(null_value_df) <- NULL
# Add percentage column
total_rows <- dim(data)[1]
null_value_df <- null_value_df %>% mutate(percentage=null_value/total_rows*100)
null_value_df
```


```{r}
# Check which column have na value > 50 %
data[, which(colMeans(is.na(data)) > 0.5)]
# Check which column did not have na value > 50 %
col_low_na_value <- data[, which(colMeans(!is.na(data)) > 0.5)]
col_low_na_value
```

```{r}
data <- data %>% select(all_of(col_low_na_value))
dim(data)
```


```{r}
# Create training (80%) and test (20%) sets for the 
set.seed(430)
split = createDataPartition(data$SalePrice, p =0.8, list = FALSE)
train = data[split, ]
test = data[-split, ]
dim(train)
dim(test)
head(train)
```
```{r}
colSums(is.na(train))
```

## Try method not convert to factor
```{r}
library(parsnip)
```

```{r}
rf_model <- rand_forest(mtry = 10, trees = 200) %>%
      set_engine("ranger", importance = "impurity") %>%
      set_mode("regression") %>%
      fit(SalePrice ~ ., data = train)
rf_model
```
```{r}
# Khong ap dung duoc khi chua convert sang factor
glmn_fit <- 
  linear_reg(penalty = 0.001, mixture = 0.5) %>% 
  set_engine("glmnet") %>%
  fit(SalePrice ~ ., data = train)
glmn_fit
```
Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : contrasts can be applied only to factors with 2 or more levels
```{r}
# Khong ap dung duoc khi chua convert sang factor
xgboost_model <- boost_tree() %>% 
            set_engine("xgboost") %>% 
            set_mode("regression") %>% 
            fit(SalePrice ~ ., data = train)
xgboost_model
```
Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : contrasts can be applied only to factors with 2 or more levels
```{r}
# Khong ap dung duoc khi co qua nhieu NA
linear_fit <- 
        linear_reg() %>% 
        set_engine("lm") %>%
        set_mode("regression") %>% 
        fit(SalePrice ~ ., data = train)
```
Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : contrasts can be applied only to factors with 2 or more levels
```{r}
# Khong ap dung duoc khi co factor 1 level
linear_fit <- 
        linear_reg() %>% 
        set_engine("lm") %>%
        set_mode("regression") %>% 
        fit(SalePrice ~ ., data = drop_na(train))

```
Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : contrasts can be applied only to factors with 2 or more levels
```{r}
# convert training data to h2o object
response="SalePrice"
predictors <- setdiff(colnames(train), response)
train_h2o_new <- as.h2o(train)
tic()
h2o.gbm <- h2o.gbm(
  x = predictors, 
  y = response,
  training_frame = train_h2o_new, 
  #validation_frame = valid_h2o,
  balance_classes = TRUE,
  nfolds=5,
  #ntrees = 1000,
  #booster = "dart",
  #normalize_type = "tree",
  
  seed = 123
)
toc() # 7 s
test_pred <-h2o.predict(h2o.gbm, newdata = test_h2o)
h2o.gbm
```

There are three main steps in creating and applying feature engineering with recipes:
VERY IMPORTANT
- recipe: where you define your feature engineering steps to create your blueprint.
- prepare: estimate feature engineering parameters based on training data.
- bake: apply the blueprint to new data.

Receipe:
- Remove near-zero variance features that are categorical (aka nominal).
- Ordinal encode our quality-based features (which are inherently ordinal).
- Center and scale (i.e., standardize) all numeric features.
- Perform dimension reduction by applying PCA to all numeric features.

While your project’s needs may vary, here is a suggested order of potential steps that should work for most problems:

- Filter out zero or near-zero variance features.
- Perform imputation if required.
- Normalize to resolve numeric feature skewness.
- Standardize (center and scale) numeric features.
- Perform dimension reduction (e.g., PCA) on numeric features.
- One-hot or dummy encode categorical features.

Functions that specify the role of the variables:

- all_predictors() applies the step to the predictor variables only
- all_outcomes() applies the step to the outcome variable(s) only
Functions that specify the type of the variables:

- all_nominal() applies the step to all variables that are nominal (categorical)
- all_numeric() applies the step to all variables that are numeric

Predictor variables: are also known as independent variables, x-variables, and input variables. A predictor variable explains changes in the response. Typically, you want to determine how changes in one or more predictors are associated with changes in the response.

Outcome variables are usually the dependent variables which are observed and measured by changing independent variables. These variables determine the effect of the cause (independent) variables when changed for different values. The dependent variables are the outcomes of the experiments determining what was caused or what changed as a result of the study.

## Try method convert to factor
```{r}
library(tictoc)
library(h2o)
h2o.init()
```

```{r}
response="SalePrice"
recipe_obj <- recipe(SalePrice ~ ., data = train) %>%
  #step_nzv(all_nominal())  %>% #Remove near-zero variance features 
  #step_knnimpute(all_predictors(), neighbors = 6) %>%  # Impute, very slow in large data, need step outside
  step_YeoJohnson(all_numeric(),-all_outcomes()) %>% # Remove skewness
  #step_integer(matches("Qual|Cond|QC|Qu")) %>% # Ordinal encoder
  step_center(all_numeric(), -all_outcomes()) %>% # center 
  step_scale(all_numeric(), -all_outcomes()) %>% # scale
  #step_dummy(all_nominal(), one_hot = TRUE) %>% 
  #step_pca(all_numeric(), -all_outcomes()) #Perform dimension reduction
  prep()
  
baked_train <- bake(recipe_obj, new_data = train)
#baked_valid <- bake(recipe_obj, new_data = valid)
baked_test <- bake(recipe_obj, new_data = test)

# convert training data to h2o object
train_h2o <- as.h2o(baked_train)
#valid_h2o <- as.h2o(baked_valid)
test_h2o <- as.h2o(baked_test)
# set the predictor names
predictors <- setdiff(colnames(baked_train), response)
```
```{r}
colSums(is.na(baked_train))
```

```{r}
# xgboost partsnip dung tot khi da convert sang factor 
xgboost_model <- boost_tree() %>% 
            set_engine("xgboost") %>% 
            set_mode("regression") %>% 
            fit(SalePrice ~ ., data = baked_train)
#xgboost_model
```

```{r}
# glmn_fit partsnip dung tot khi da convert sang factor , chap nhan NA value
glmn_fit <- 
  linear_reg(penalty = 0.001, mixture = 0.5) %>% 
  set_engine("glmnet") %>%
  set_mode("regression") %>% 
  fit(SalePrice ~ ., data = baked_train)
# glmn_fit
```

```{r}
# linear regression cannot work, may be NA value
linear_fit <- 
        linear_reg() %>% 
        set_engine("lm") %>%
        set_mode("regression") %>% 
        fit(SalePrice ~ ., data = baked_train)
```
Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : contrasts can be applied only to factors with 2 or more levels
```{r}
linear_fit <- 
        linear_reg() %>% 
        set_engine("lm") %>%
        set_mode("regression") %>% 
        fit(SalePrice ~ ., data = drop_na(baked_train))
```
Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : contrasts can be applied only to factors with 2 or more levels
```{r}
tic()
h2o.gbm <- h2o.gbm(
  x = predictors, 
  y = response,
  training_frame = train_h2o, 
  #validation_frame = valid_h2o,
  balance_classes = TRUE,
  nfolds=5,
  #ntrees = 1000,
  #booster = "dart",
  #normalize_type = "tree",
  
  seed = 123
)
toc() # 7 s
test_pred <-h2o.predict(h2o.gbm, newdata = test_h2o)
h2o.gbm
```

#3. Benchmark method
```{r}
library(tidymodels)
data(ames)
#ames <- mutate(ames, Sale_Price = log10(Sale_Price))
ames
```


```{r}
colSums(is.na(ames))
```

```{r}
#ames_split <- initial_split(ames, prop = 0.80, strata = Sale_Price)
#ames_train <- training(ames_split)
#ames_test  <-  testing(ames_split)
```

```{r}
# Create training (80%) and test (20%) sets for the 
set.seed(430)
split = createDataPartition(data$SalePrice, p =0.8, list = FALSE)
train = data[split, ]
test = data[-split, ]
dim(train)
dim(test)
head(train)
```

```{r}
blueprint <- recipe(SalePrice ~ ., data = train_data) %>%
  step_nzv(all_nominal())  %>% #Remove near-zero variance features 
  #step_knnimpute(all_predictors(), neighbors = 6) %>%  # Impute
  step_YeoJohnson(all_numeric(),-all_outcomes()) %>% # Remove skewness
  #step_integer(matches("Qual|Cond|QC|Qu")) %>% # Ordinal encoder
  step_center(all_numeric(), -all_outcomes()) %>% # center 
  step_scale(all_numeric(), -all_outcomes()) # scale
  #step_dummy(all_nominal(), one_hot = TRUE) %>% 
  #step_pca(all_numeric(), -all_outcomes()) #Perform dimension reduction
prepare <- prep(blueprint, training = train_data)
```


```{r}
ames_rec <- 
  recipe(Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built + Bldg_Type + 
           Latitude + Longitude, data = ames_train) %>%
  step_log(Gr_Liv_Area, base = 10) %>% 
  step_other(Neighborhood, threshold = 0.01) %>% 
  step_dummy(all_nominal()) %>% 
  step_interact( ~ Gr_Liv_Area:starts_with("Bldg_Type_") ) %>% 
  step_ns(Latitude, Longitude, deg_free = 20)
```


```{r}
```


```{r}
```

