---
title: "Untitled"
output: html_document
---
```{r}
library(tidyverse)
library(forecast)
```

```{r}
# Check all file in this zip folder
unzip("all_stocks_5yr.csv.zip", list=TRUE)
```

```{r}
s_data <- read.csv(unz("all_stocks_5yr.csv.zip", "all_stocks_5yr.csv"))
head(s_data)
tail(s_data)
```
```{r}
length(unique(s_data$Name))
```
# 0.4 Data overview

```{r}
summary(s_data)
```


```{r}
sum(is.na(s_data))
```

# 0.5 Data cleaning

```{r}
s_data[is.na(s_data)]
s_data[is.na(s_data)] <- 0
s_data
```


```{r}
s_data$date <- as.Date(s_data$date, format = "%Y-%m-%d")
```

# 0.7 Time Series Analysis
```{r}
i_stock <- filter(s_data, Name == "PSA")
str(i_stock)
```
# 0.8 Create time series
We will use tsclean and ts function of R to create a time series.

tsclean() is a convenient method for outlier removal and inputing missing values

ts() is used to create time-series objects

```{r}
summary(i_stock)
```
# 0.8 Create time series
```{r}
## Create a daily Date object
inds <- seq(as.Date("2012-08-13"), as.Date("2017-08-11"), by = "day")
head(inds)
as.numeric(format(inds[1], "%j"))
```

```{r}
col_idx <- "high"
i_ts <- as.numeric(i_stock[,col_idx]) %>%
    tsclean(replace.missing = TRUE, lambda = NULL) %>%
    ts(start = c(2012, as.numeric(format(inds[1], "%j"))),
             frequency = 365.5)
```


```{r}
head(i_ts)
tail(i_ts)
```

# 0.9 Plotting Time Series - High

```{r}
plot.ts(i_ts, xlab = "Time", ylab = "High value", main = "Time Series", col = "red")
```
# 0.10 Stationarity

What is stationary time series?

A stationary process has a mean and variance that do not change overtime and the process does not have trend.

The above time series does not look stationary.

To confirm that we will use “Dickey-Fuller test” to determine stationarity.

Dickey-Fuller test for variable
```{r}
#library(tseries)
tseries::adf.test(i_ts, alternative = "stationary", k = 0)
```

# 0.11 Decomposing Time Series
Decomposing a time series involves separating the time series into trend and irregular components.
```{r}
i_tscomponents <- decompose(i_ts)
plot(i_tscomponents, col = "red")
```
# 0.12 Differencing a Time Series
Differencing is a common solution used to stationarize the variable. We will perform differencing using R function diff.
```{r}
i_tsdiff1 <- diff(i_ts, differences=1)
plot.ts(i_tsdiff1, col = "red")
```
The time series (above) appears to be stationary.

# 0.13 Selecting a Candidate ARIMA Model

The next step is to select appropriate ARIMA model, which means finding the most appropriate values of p and q for an ARIMA(p,d,q) model. You usually need to examine the correlogram and partial correlogram of the stationary time series for this. To plot a correlogram and partial correlogram, we can use the acf() and pacf() functions in R, respectively.

```{r}
acf(i_tsdiff1, lag.max=60)             # plot a correlogram
```


```{r}
acf(i_tsdiff1, lag.max=60, plot=FALSE) # get the autocorrelation values
```


```{r}
pacf(i_tsdiff1, lag.max=60)             # plot a partial correlogram
```


```{r}
pacf(i_tsdiff1, lag.max=60, plot=FALSE) # get the partial autocorrelation values
```

#0.14 Fitting an ARIMA Model
R provides a function auto.arima, which returns best ARIMA model according to either AIC, AICc or BIC value. The function conducts a search over possible model within the order constraints provided.


```{r}
i_tsarima <- auto.arima(i_ts, max.p = 3, max.q = 3, max.d = 3)
i_tsarima
```

# 0.15 Forecasting using an ARIMA Model
```{r}
i_tsforecasts <- forecast(i_tsarima, h = 60)
plot(i_tsforecasts, col = "red")
```


```{r}
plot.ts(i_tsforecasts$residuals)            # make time plot of forecast errors
```


```{r}
ggplot(data.frame(residuals = i_tsforecasts$residuals), aes(residuals)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "red", alpha = 0.3) + geom_density()# make a histogram
```
The forecast errors seem to be normally distributed with mean zero and constant variance, the ARIMA model does seem to provide an adequate predictive model

Here we looked at how to best fit ARIMA model to univariate time series. Next thing that I’ll work on is Multivariate Time Series Forecasting using neural net.

```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

