---
title: "6.Series Time series 5 minutes"
output: html_document
---
# Time Series in 5-Minutes, Part 1: Data Wrangling and Rolling Calculations
```{r}
library(tidyverse)
library(tidyquant) 
library(timetk)
```


```{r}
FANG
```


```{r}
FANG %>%
  group_by(symbol) %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)
```


```{r}
FANG %>%
  group_by(symbol) %>%
  plot_time_series(date, volume, .facet_ncol = 2, .interactive = FALSE)
```
```{r}
FANG
```


```{r}
FANG %>%
  group_by(symbol) %>%
  summarise_by_time(
    date, .by = "quarter",
    volume = SUM(volume)
  )
```


```{r}
FANG %>%
  group_by(symbol) %>%
  summarise_by_time(
    date, .by = "quarter",
    volume = SUM(volume)
  ) %>%
  plot_time_series(date, volume, .facet_ncol = 2, .interactive = FALSE, .y_intercept = 0)
```

Objective: Get the first value in each month

We can use FIRST() to get the first value, which has the effect of reducing the data (i.e. smoothing). We could use AVERAGE() or MEDIAN().
Use the summarization by time: .by = "month" to aggregate by month.

```{r}
FANG %>%
  group_by(symbol) %>%
  summarise_by_time(
    date, .by = "month",
    adjusted = FIRST(adjusted)
  ) %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)
```

Time Range Filtering
Objective: Get the adjusted stock prices in the 3rd quarter of 2013.

.start_date = "2013-09": Converts to “2013-09-01
.end_date = "2013": Converts to “2013-12-31
A more advanced example of filtering using %+time and %-time is shown in “Padding Data: Low to High Frequency”.
```{r}
FANG %>%
  group_by(symbol) %>%
  filter_by_time(date, "2013-09", "2013") %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)

```

Fill in Gaps
```{r}
FANG %>%
  group_by(symbol) %>%
  pad_by_time(date, .by = "auto") # Guesses .by = "day"
```

Low to High Frequency
```{r}
FANG %>%
  group_by(symbol) %>%
  pad_by_time(date, .by = "hour") %>%
  mutate_at(vars(open:adjusted), .funs = ts_impute_vec, period = 1) %>%
  filter_by_time(date, "start", FIRST(date) %+time% "1 month") %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE) 
```

Sliding (Rolling) Calculations
```{r}
# Make the rolling function
roll_avg_30 <- slidify(.f = AVERAGE, .period = 30, .align = "center", .partial = TRUE)
roll_avg_30
```


```{r}
# Apply the rolling function
FANG %>%
  select(symbol, date, adjusted) %>%
  group_by(symbol) %>%
  # Apply Sliding Function
  mutate(rolling_avg_30 = roll_avg_30(adjusted)) %>%
  pivot_longer(cols = c(adjusted, rolling_avg_30)) %>%
  plot_time_series(date, value, .color_var = name,
                   .facet_ncol = 2, .smooth = FALSE, 
                   .interactive = FALSE)
```


```{r}
FANG %>%
  select(symbol, date, adjusted) %>%
  group_by(symbol) %>%
  # Apply roll apply Function
  mutate(rolling_avg_30 = slidify_vec(adjusted,  ~ AVERAGE(.), 
                                      .period = 30, .partial = TRUE))
```


```{r}
# Rolling regressions are easy to implement using `.unlist = FALSE`
lm_roll <- slidify(~ lm(..1 ~ ..2 + ..3), .period = 90, 
                   .unlist = FALSE, .align = "right")
FANG %>%
  select(symbol, date, adjusted, volume) %>%
  group_by(symbol) %>%
  mutate(numeric_date = as.numeric(date)) %>%
  # Apply rolling regression
  mutate(rolling_lm = lm_roll(adjusted, volume, numeric_date)) %>%
  filter(!is.na(rolling_lm))
```

# Time Series in 5-Minutes, Part 6: Modeling Time Series Data
```{r}
remotes::install_github("business-science/modeltime")
```

```{r}
install.packages("modeltime",dependencies = T)
library(tidymodels)
library(modeltime)
library(tidyverse)
library(lubridate)
library(timetk)
# This toggles plots from plotly (interactive) to ggplot (static)
interactive <- TRUE
```

```{r}
m4_monthly
```


```{r}
summary(m4_monthly)
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


