---
title: "Untitled"
output: html_document
---
FAIL



https://www.business-science.io/code-tools/2017/07/09/sweep-0-1-0.html

oad the following packages:

forecast: Has excellent modeling functions such as auto.arima(), ets() and bats() and the forecast() function for predicting future observations.
sweep: Tidies the output of forecast functions using a similar strategy as the broom package.
timekit (convert to timetk): Coercion function tk_ts() for converting a tibble to ts while maintaining time-based data.
tidyquant: Used to get FRED data and for its ggplot2 theme.
geofacet: Really useful facet_geo() function to visualize facets organized by geography.
```{r}
install.packages("geofacet",dependencies = TRUE)
#remotes::install_github("hafen/geofacet")
```

```{r}

# Load packages
library(forecast)   # Most popular forecasting pkg
library(sweep)      # Broom tidiers for forecast pkg
library(timetk)    # Working with time series in R
library(tidyquant)  # Get's data from FRED, loads tidyverse behind the scenes
library(geofacet)   # facet_geo() for visualizing facets organized as states
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

