---
title: "Untitled"
output: html_document
---

FAIL


https://www.business-science.io/code-tools/2017/03/19/tidyquant-quandl-integration.html

```{r}
#install.packages("corrr")
# Loads tidyquant, tidyverse, lubridate, quantmod, TTR, xts, zoo, PerformanceAnalytics
library(tidyverse)
library(tidyquant)
library(broom) # Use `tidy` and `glance` functions
library(corrr) # tidy correlations
```


```{r}
quandl_api_key("yz7qGzikAuQL9wn7rrX-")
```


```{r}
stock_list_quandl <- tribble(
    ~code,          ~symbol,
    "WIKI/AAPL", "AAPL",
    "WIKI/F",    "F",
    "WIKI/GE",   "GE",
    "WIKI/MSFT", "MSFT"
)
stock_list_quandl
```


```{r}
stock_returns_quandl <- stock_list_quandl %>%
    tq_get(get          = "quandl",
           from         = "2007-01-01",
           to           = "2016-12-31",
           transform    = "rdiff",
           collapse     = "monthly",
           column_index = 11) %>%
    rename(monthly.returns = adj.close)
stock_returns_quandl
```
Collecting Fama French 3-Factor Monthly Data

Next, we need to get the Fama French data. Suppose we don’t know exactly what we are looking for. We’ll use the function, quandl_search(), to query the Quandl API (a wrapper for Quandl.search()). We can search within the R console by setting query to a descriptive value. We’ll set per_page = 5 to get the top 5 results. We’ll set silent = TRUE to turn off the meta data output (in practice it may be beneficial to leave this easy-to-read option on). The results returned contain the “id”, dataset_code, “database_code”, “name”, “description”, etc, which gives us both insight into the data set contents and the information needed to retrieve. I’ve removed “description” to make it easier to view the information.

```{r}
quandl_search(query = "FAMA FRENCH", per_page = 5, silent = TRUE) %>%
    select(-description)
```


```{r}
# Get Fama French 3 Factor Data
fama_french_3_M <- "KFRENCH/FACTORS_M" %>%
    tq_get(get      = "quandl",
           collapse = "monthly")
fama_french_3_M
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


i```{r}
```

