

# 1.0 LIBRARIES ----
```{r}
# Core & Viz
library(vroom)
library(tidyverse)
library(tidyquant)
library(plotly)

# Modeling
library(recommenderlab)
library(arules)
library(arulesViz)
library(SmartEDA)
```

# 2.0 DATA ----
```{r}
# 2.0 DATA ----
orders_products_tbl <- vroom("/home/dnn/Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Data/order_products__train.csv", delim = ",") # 24 MB
orders_products_tbl

orders_tbl <- vroom("/home/dnn/Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Data/orders.csv", delim = ",") # 109 MB
orders_tbl

products_tbl <- vroom("/home/dnn/Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Data/products.csv", delim = ",") # 2 MB
products_tbl

aisles_tbl <- vroom("/home/dnn/Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Data/aisles.csv", delim = ",")
aisles_tbl

departments_tbl <- vroom("/home/dnn/Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Data/departments.csv", delim = ",")
departments_tbl

dim(orders_products_tbl) # 1,384,617       4
dim(orders_tbl) # 3,421,083       7
```

# 3.0 DATA UNDERSTANDING ----
```{r}
orders_combined_tbl <- orders_products_tbl %>% 
    left_join(orders_tbl) %>% # join by order_id
    left_join(products_tbl) %>% # join by product_id
    left_join(aisles_tbl) %>% # join by aisle_id
    left_join(departments_tbl) %>% # join by department_id
    select(eval_set, user_id, 
           contains("order"), contains("product"), 
           contains("aisle"), contains("department"), everything()) 
orders_combined_tbl %>% glimpse()
```


```{r}
ExpData(data=orders_combined_tbl,type=1)
```


```{r}
ExpData(data=orders_combined_tbl,type=2)
```
# General EDA

```{r}
#ExpNumStat(orders_combined_tbl,by="A",gp=NULL,Qnt=seq(0,1,0.1),MesofShape=2,Outlier=TRUE,round=2,Nlim=10)
```


```{r}
ExpNumViz(orders_combined_tbl,target=NULL,nlim=10,Page=c(2,2),sample=4)
```


```{r}
plot2 <- ExpCatViz(orders_combined_tbl,target=NULL,col ="slateblue4",clim=10,margin=2,Page = c(2,1),#sample=4
                   )
plot2
```


```{r}
```

# 3.1 Which products are purchased most frequently? ----
```{r}
head(orders_combined_tbl)
```
Rows: 1,384,617
Columns: 15
```{r}
# product name = product id
orders_combined_tbl %>%
    count(product_name, product_id, aisle, department) %>%
    arrange(desc(n))
# Tu 1tr384 row giam xuong con 39,123 rows: nhung product_id (name) nao hay dung se duoc gop chung lai va count luon
```
```{r}
 orders_combined_tbl %>%
    count(product_name, product_id, aisle, department) %>%
    arrange(desc(n)) %>%
    mutate(
        pct = n / sum(n),
        cumulative_pct = cumsum(pct), # Cong tat ca pct tu 1 --> n giong nhu pareto chart
        popular_product = ifelse(cumulative_pct <= 0.5, "Yes", "No")
    ) %>%
    rowid_to_column(var = "rank") 
```

```{r}
item_frequency_tbl <- orders_combined_tbl %>%
    count(product_name, product_id, aisle, department) %>%
    arrange(desc(n)) %>%
    mutate(
        pct = n / sum(n),
        cumulative_pct = cumsum(pct),
        popular_product = ifelse(cumulative_pct <= 0.5, "Yes", "No")
    ) %>%
    rowid_to_column(var = "rank") %>%
    mutate(label_text = str_glue("Rank: {rank}
                                 Product: {product_name}
                                 ProductID: {product_id}
                                 Aisle: {aisle}
                                 Department: {department}
                                 Count: {n}
                                 Pct: {scales::percent(pct)}
                                 Cumulative Pct: {scales::percent(cumulative_pct)}")) 
    

item_frequency_tbl
```

```{r}
 item_frequency_tbl %>%
    slice(1:5000) %>% # Chi lay 5000 sp nhieu nhat thoi
    ggplot(aes(rank, n)) + # name la rank id, khong phai product_name, theo n
    geom_point(aes(size = n, color = popular_product, text = label_text), alpha = 0.2)
```
```{r}
summary(item_frequency_tbl %>% select(n))
```

Popular product: banana (buy 18726 times)
Normally all product was buy 5 times
```{r}
# g <- item_frequency_tbl %>%
#     slice(1:5000) %>%
#     ggplot(aes(rank, n)) +
#     geom_point(aes(size = n, color = popular_product, text = label_text), alpha = 0.2) +
#     theme_tq() +
#     scale_color_tq() +
#     theme(legend.direction = "vertical", 
#           legend.position  = "right") +
#     labs(title = "Item Frequency", 
#          subtitle = "Top Items Account For Majority Of Purchases")
# 
# ggplotly(g, tooltip = "text")
```
# 3.2 Do Customers Purchase More Frequently? ----
# 3.3 Do Certain Customers Buy More Products? ----
```{r}
user_frequency_tbl <- orders_combined_tbl %>% 
                        select(user_id) %>% 
                        count(user_id) %>% 
                        arrange(desc(n)) %>% 
                        mutate(
                                pct = n / sum(n),
                                cumulative_pct = cumsum(pct),
                                popular_customer = ifelse(cumulative_pct <= 0.5, "Yes", "No")
                            ) %>%
                            rowid_to_column(var = "rank") 
user_frequency_tbl
```
```{r}
user_frequency_tbl %>%
    slice(1:5000) %>%
    ggplot(aes(rank, n)) +
    geom_point(aes(size = n, color = popular_customer), alpha = 0.2)
```
```{r}
summary(user_frequency_tbl %>% select(n))
```
Customer usually order 9 times (max: 80 times)


```{r}
# g <- user_frequency_tbl %>%
#     slice(1:5000) %>%
#     ggplot(aes(rank, n)) +
#     geom_point(aes(size = n, color = popular_customer), alpha = 0.2) +
#     theme_tq() +
#     scale_color_tq() +
#     theme(legend.direction = "vertical", 
#           legend.position  = "right") +
#     labs(title = "User Frequency", 
#          subtitle = "How Often Do You Shop? - No Frequency! Everyone is 1st time.")
# 
# ggplotly(g)
```

# 4.0 CONDENSE USER-ITEM / TRANSACTION-ITEM MATRIX FOR EVALUATION ----
```{r}
# 4.1 Popular Products ----
top_products_vec <- item_frequency_tbl %>%
    filter(popular_product == "Yes") %>%
    pull(product_name)
head(top_products_vec)
```


```{r}
# Use names to filter 
top_products_basket_tbl <- orders_combined_tbl %>%
    filter(product_name %in% top_products_vec) 
head(top_products_basket_tbl)
```
```{r}
top_products_basket_tbl %>% glimpse()
```


```{r}
# 4.2 Large Baskets ----
top_users_vec <- user_item_frequency_tbl %>%
    filter(rank < 2500) %>%
    pull(user_id)
head(top_users_vec)
```


```{r}
market_basket_condensed_tbl <- top_products_basket_tbl %>%
    filter(user_id %in% top_users_vec) 

head(market_basket_condensed_tbl)
```

# 5.0 MARKET BASKET ANALYSIS ----
```{r}
# 5.1.1 "Binary Ratings Matrix"
# - Did basket contain an item (Yes/No encoded as 1-0)
# - See also "Real Ratings Matrix" for "Amazon"-style ratings 1-5

user_item_tbl <- market_basket_condensed_tbl %>%
    select(user_id, product_name) %>%
    mutate(value = 1) %>%
    spread(product_name, value, fill = 0)
dim(user_item_tbl) #  2498  847
head(user_item_tbl)
```


```{r}
user_item_rlab <- user_item_tbl %>%
    select(-user_id) %>%
    as.matrix() %>%
    as("binaryRatingMatrix")

user_item_rlab
```


```{r}
# 5.1.2 Relationship with arules package

user_item_rlab@data

user_item_rlab@data %>% summary()

user_item_rlab@data %>% glimpse()
```


```{r}
# dev.off()
itemFrequencyPlot(user_item_rlab@data, topN=30, type="absolute",
                  xlab = "Items", ylab = "Frequency (absolute)",
                  col = "steelblue",
                  main = "Absolute Frequency Plot")
```
```{r}
# 5.2 CREATE EVALUATE SHEME(S) (RECIPES) ----
recommenderRegistry$get_entries()

eval_recipe <- user_item_rlab %>%
    evaluationScheme(method = "cross-validation", k = 5, given = -1)

eval_recipe
```
evaluationScheme:
Creates an evaluationScheme object from a data set. The scheme can be a simple split into training and test data, k-fold cross-evaluation or using k independent bootstrap samples.

```{r}
# 5.2.1 Association Rules

algorithms_list <- list(
    "association rules1"   = list(name  = "AR", 
                                  param = list(supp = 0.01, conf = 0.01)),
    "association rules2"  = list(name  = "AR", 
                                 param = list(supp = 0.01, conf = 0.1)), # Best in this example
    "association rules3"  = list(name  = "AR", 
                                 param = list(supp = 0.01, conf = 0.5)),
    "association rules4"  = list(name  = "AR", 
                                 param = list(supp = 0.1, conf = 0.5))
)
```


```{r}
# !!! WARNING - Long Running Script !!!
library(tictoc)
tic()
results_rlab_arules <- eval_recipe %>%
    recommenderlab::evaluate(
        method    = algorithms_list, 
        type      = "topNList", 
        n         = 1:10)
toc() # 126.897 sec elapsed
```


```{r}
# Load from save rds file
results_rlab_arules <- read_rds("~/Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Modeling_Results/results_arules.rds")
plot(results_rlab_arules, annotate = TRUE)
```


```{r}
# 5.2.2 All Algorithms ----

algorithms_list <- list(
    "random items"        = list(name  = "RANDOM", # base line, just guest random item
                                 param = NULL),
    "popular items"       = list(name  = "POPULAR", # just throw popular items over the time (top 10 ?)
                                 param = NULL),
    "user-based CF"       = list(name  = "UBCF", # nn : nearest neighbord , Best in this model
                                 param = list(method = "Cosine", nn = 500)),
    "item-based CF"       = list(name  = "IBCF", # k :  , second best in this model
                                 param = list(k = 5)),
    "association rules2"  = list(name  = "AR",  # association rule : detail how people purchase sth
                                 param = list(supp = 0.01, conf = 0.1))
)
```


```{r}
# !!! WARNING - Long Running Script !!!
tic()
results_rlab <- eval_recipe %>%
    recommenderlab::evaluate(
        method    = algorithms_list, 
        type      = "topNList", 
        n         = 1:10)
toc() # 76.632 sec elapsed
```


```{r}
# Read form save model
results_rlab <- read_rds("~//Data_science/Git/Business science/Marketing analytics/lab_11_market_basket_analysis/learning_lab_11_market_basket_analysis/00_Modeling_Results/results_all_models.rds")

plot(results_rlab, annotate = TRUE)
```
# 6.0 BUILD MODELS ----

```{r}
# 6.1 ASSOCIATION RULES ----
model_ar <- recommenderlab::Recommender(
    data = user_item_rlab, 
    method = "AR", 
    param = list(supp = 0.01, conf = 0.10))
model_ar
```


```{r}
# 6.2 UBCF ----
model_ucbf <- recommenderlab::Recommender(
    data = user_item_rlab, 
    method = "UBCF", 
    param  = list(method = "Cosine", nn = 500))
model_ucbf
```

# 7.0 INVESTIGATE RELATIONSHIPS ----
```{r}
# 7.1 INTERACTIVE ----
rules <- model_ar@model$rule_base
inspectDT(rules)
```

Sort by lift (high is more association)
3,278 association rule
LHS: sparkling lemon water --> recommend Lime sparkling water

```{r}
plotly_arules(rules, method = "scatterplot", 
              marker = list(opacity = .7, size = ~lift), 
              colors = c("blue", "green"))
```

Inspect rule: a lot of rule for recommendation in this plot (high lift, better recommendation)
```{r}
# 7.2 STATIC ----
sort(rules, by = "lift", decreasing = TRUE)[1:20] %>%
    inspect() 

plot(rules, method = "graph")
```
Strawberries with buy Banana, Organic Baby will buy organic strawberries, lot of things will buy Bag of Organic Bananas

```{r}
plot(model_ar@model$rule_base, method = "graph", 
     control=list(layout=igraph::in_circle()))
```

# 8.0 PREDICTION ----
```{r}
new_user_basket <- c("Banana", "Organic Whole Milk")
tibble(items = user_item_rlab@data %>% colnames()) %>% # 846 items
    mutate(value = as.numeric(items %in% new_user_basket)) %>% # 0 if items not in new_user_basket, 1 if items in new_user_basket
    spread(key = items, value = value)
```

```{r}
# 8.1 PREPARE NEW DATA ----
new_user_basket <- c("Banana", "Organic Whole Milk")

new_user_basket_rlab <- tibble(items = user_item_rlab@data %>% colnames()) %>% # 846 items
    mutate(value = as.numeric(items %in% new_user_basket)) %>%
    spread(key = items, value = value) %>%
    as.matrix() %>%
    as("binaryRatingMatrix")

new_user_basket_rlab


```


```{r}
# 8.2 ASSOCIATION RULES ----

prediction_ar <- predict(model_ar, newdata = new_user_basket_rlab, n = 3) # recommen 3 items

tibble(items = prediction_ar@itemLabels) %>%
    slice(prediction_ar@items[[1]])
```


```{r}
# 8.3 UBCF ----

prediction_ucbf <- predict(model_ucbf, newdata = new_user_basket_rlab, n = 3)

tibble(items = prediction_ucbf@itemLabels) %>%
    slice(prediction_ucbf@items[[1]])
```


```{r}
```


```{r}
```

```{r}
```


```{r}
```


```{r}
```

