---
title: "Lab 23 - BigQuery for Google Analytics"
author: "Business Science"
date: "11/20/2019"
output: 
    html_document:
        theme: flatly
        df_print: paged
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo    = TRUE,
    message = FALSE,
    warning = FALSE)
```

## 1.0 Libraries & Setup

To get Started:

- Create a Google Cloud Platform Account. Navigate to BigQuery. Add a dataset. 

- Make sure to use the [RStudio Preview Version](https://rstudio.com/products/rstudio/download/preview/) for this Learning Lab. Otherwise you may get an "Error: Option error has NULL value".

```{r}
# Libraries ----
#install.packages("bigrquery")
# Databases
library(bigrquery)
library(DBI)
library(connections)
library(jsonlite)

# Parallel Processing
library(furrr)
library(tictoc)

# Core
library(tidyverse)
library(tidyquant)
library(dbplyr)
library(lubridate)
library(plotly)
```

## 2.0 Connection 

```{r}
# Connect to BigQuery 
bigrquery::bq_auth() # This will use your Google Account to setup billing info. There will be zero cost to run this analysis. 

con <- dbConnect(
    bigrquery::bigquery(),
    project = "bigquery-public-data",
    dataset = "google_analytics_sample",
    billing = "YOUR PROJECT ID HERE"
)

con
```

```{r}
# View the Connection in Connections Pane
connection_view(con)
```

## 3.0 Data Exploration

### 3.1 Inspect the BigQuery Google Analytics Tables & Table Structure

```{r}
# List the tables
dbListTables(con) %>% length()
```

```{r, error=TRUE}
# Show the error - file size too large
ga_sessions_20160801 <- tbl(con, "ga_sessions_20160801") %>% collect()
ga_sessions_20160801
```

```{r}
# Check out data format - Nested List Structure
# - Similar to NoSQL
tbl(con, "ga_sessions_20160801") %>% glimpse()
```

### 3.2 View as JSON

```{r}
# JSON
# - Take a look at "totals" list column
# - Each visitor session has 
totals_tbl <- tbl(con, "ga_sessions_20160801") %>%
    head(1) %>%
    select(visitId, totals) %>%
    collect()
```

```{r}
totals_tbl
```



```{r}
# View as JSON
totals_tbl %>% toJSON() %>% prettify()
```


### 3.3 View as Nested Tibble

```{r}
# Tibble - Can also inspect as a nested tibble
# - Filter to get session info first visitID == 1470117657
hits_tbl <- tbl(con, "ga_sessions_20160801") %>%
    filter(visitId == 1470117657) %>%
    select(visitId, hits) %>%
    collect() 
```

```{r}
# VisitId == 1470117657
hits_tbl
```


```{r}
# Drill into hits column for visitID == 1470117657
hits_tbl %>% pluck("hits", 1)
```

```{r}
# Drill into hits > pages for visitID == 1470117657
hits_tbl %>% 
    pluck("hits", 1, "page") %>% 
    toJSON() %>% 
    prettify() %>%
    fromJSON() %>% 
    unnest(cols = pagePath:pagePathLevel4)
```


## 4.0 Iterating with BigQuery

### Question 1 - How many unique visitors per day? 

#### Method 1 - Sequential Iteration with `map()` Functions. 

- Pros - Can utilize `dplyr`
- Cons - Takes 35 seconds to count unique visits for 10-days.

```{r, eval=FALSE}
# Iterate through each table sequentially
tic()
dbListTables(con) %>%
    
    # First 10 only 
    .[1:10] %>%
    
    # Collect counts
    map_dfr(.f = function(x) {
        tbl(con, x) %>%
            distinct(fullVisitorId) %>%
            count() %>%
            collect()
    })
toc()
```

#### Method 2 - Process in Parallel with `furrr`

- Pros - Can utilize `dplyr`
- Cons - Takes __6 seconds__ to count unique visits for 10-days.

```{r, eval=F}
plan("multisession")

tic()
dbListTables(con) %>%
    .[1:10] %>%
    future_map_dfr(.f = function(x) {
        tbl(con, x) %>%
            distinct(fullVisitorId) %>%
            count() %>%
            collect()
    }, .progress = TRUE)
toc()
```

#### Method 3 - Use BigQuery Wildcard and Table Suffixes

- Pros: Much more scalable - takes __14 seconds for all 365-days__
- Cons: For nested data, we need to know __BigQuery Standard SQL__

```{r, eval=F}
tic()
unique_visitors_tbl <- tbl(con, "ga_sessions_*") %>%
    # filter(`_TABLE_SUFFIX` %>% between("20160801", "20160810")) %>%
    distinct(date, fullVisitorId) %>%
    count(date) %>%
    collect() 
toc()

unique_visitors_tbl
```

```{r, eval=F}
# Visualize Unique Visitor Traffic
g <- unique_visitors_tbl %>%
    mutate(date = ymd(date)) %>%
    arrange(desc(date)) %>%
    ggplot(aes(date, n)) +
    geom_line() +
    expand_limits(y = 0) +
    labs(title = "Daily Active Users - Unique Visitor IDs")

ggplotly(g)
```


## 5.0 Big Query SQL - Introduction

### Question 2 - Total Number of Transactions Over Time 

Need to use BigQuery Standard SQL because of the nested `totals.transactions` list column. 

```{r}
transactions_by_date_query <- "
SELECT date, SUM ( totals.transactions ) AS total_transactions
FROM `bigquery-public-data.google_analytics_sample.ga_sessions_*`
GROUP BY date
ORDER BY total_transactions DESC;
"

transactions_by_date_tbl <- dbGetQuery(con, transactions_by_date_query)
```

```{r}
g <- transactions_by_date_tbl %>%
    mutate(date = ymd(date)) %>%
    arrange(desc(date)) %>%
    
    ggplot(aes(date, total_transactions)) +
    geom_line() +
    expand_limits(y = 0) +
    labs(title = "Transactions Over Time")

ggplotly(g)
```

### Question 3 - Transactions by Referral / Medium 

```{r}
traffic_tbl <- tbl(con, "ga_sessions_20160801") %>%
    filter(visitId == 1470117657) %>%
    select(visitId, trafficSource) %>%
    collect()
```

```{r}
traffic_tbl %>%
    pluck("trafficSource") %>%
    toJSON() %>%
    fromJSON() %>%
    unnest(referralPath:campaignCode)
```

```{r}
transactions_by_medium_query <- "
SELECT date, trafficSource.medium, SUM ( totals.transactions ) AS total_transactions
FROM `bigquery-public-data.google_analytics_sample.ga_sessions_*`
GROUP BY date, medium
ORDER BY total_transactions DESC;
"

transactions_by_medium_tbl <- dbGetQuery(con, transactions_by_medium_query)
```

```{r}
g <- transactions_by_medium_tbl %>%
    mutate(date = ymd(date)) %>%
    
    ggplot(aes(date, total_transactions, color = medium, group = medium)) +
    geom_line()

ggplotly(g)
```

## 6.0 BigQuery SQL - Unnesting & Joining Multiple Queries in BigQuery 

### Question 4 - Which Page Paths Leading to Transactions?

```{r}
page_path_query <- "
SELECT fullVisitorId, visitId, visitNumber, h.hitNumber AS hitNumber, h.page.pagePath AS pagePath
FROM `bigquery-public-data.google_analytics_sample.ga_sessions_*`

LEFT JOIN UNNEST(hits) AS h

WHERE _TABLE_SUFFIX BETWEEN '20170701' AND '20170731'
AND h.type='PAGE'

ORDER BY fullVisitorId, visitId, visitNumber, hitNumber
"

page_path_tbl <- dbGetQuery(con, page_path_query)
```

```{r}
page_path_tbl
```


```{r}
transaction_visitId_query <- "
SELECT visitId, SUM( totals.transactionRevenue ) AS total_transaction_revenue
FROM `bigquery-public-data.google_analytics_sample.ga_sessions_*`
WHERE _TABLE_SUFFIX BETWEEN '20170701' AND '20170731'
GROUP BY visitId
ORDER BY total_transaction_revenue DESC
"

transaction_visitId_tbl <- dbGetQuery(con, transaction_visitId_query)

```

```{r}
transaction_visitId_tbl
```


```{r}
join_query <- str_glue(
"
SELECT * FROM ( {page_path_query} )
LEFT JOIN ( {transaction_visitId_query} ) 
USING (visitId)
"
) 

join_query
```

```{r}
page_path_transactions_joined_tbl <- dbGetQuery(con, join_query)
```

```{r}
page_path_transactions_joined_tbl %>%
    select(total_transaction_revenue, everything()) %>%
    arrange(desc(total_transaction_revenue)) %>%
    mutate(total_transaction_revenue = total_transaction_revenue * 1e-6) 
```


```{r}
successful_transactions_tbl <- page_path_transactions_joined_tbl %>%
    filter(total_transaction_revenue > 0) %>%
    select(total_transaction_revenue, everything()) %>%
    mutate(total_transaction_revenue = total_transaction_revenue * 1e-6) 

successful_transactions_tbl
```

```{r}
success_page_path_summary_tbl <- successful_transactions_tbl %>%
    group_by(pagePath) %>%
    summarize(
        n = n(),
        median_hit_number   = median(hitNumber),
        median_visit_number = median(visitNumber)
    ) %>%
    ungroup() %>%
    arrange(desc(n))

success_page_path_summary_tbl
```

```{r}
g <- success_page_path_summary_tbl %>%
    slice(1:10) %>%
    arrange(median_hit_number) %>%
    mutate(pagePath = as_factor(pagePath)) %>%
    
    ggplot(aes(pagePath, median_hit_number, fill = n)) +
    geom_col() +
    coord_flip() +
    theme_tq() +
    scale_fill_viridis_c() +
    labs(
        title = "Transaction Page Path Funnel",
        fill  = "Success Count"
    )

ggplotly(g)
```

```{r}
g <- success_page_path_summary_tbl %>%
    slice(1:10) %>%
    arrange(median_hit_number) %>%
    mutate(pagePath = as_factor(pagePath)) %>%
    
    ggplot(aes(pagePath, n, fill = n)) +
    geom_col() +
    coord_flip() +
    theme_tq() +
    scale_fill_viridis_c() +
    labs(
        title = "Most Important Step in Funnel",
        fill  = "Success Count"
    )

ggplotly(g)
```

