---
title: "Untitled"
output: html_document
---

```{r}
library(readxl)
library(tidyverse)
```

```{r}
df <- read_excel(path="/home/dnn/Data_science/Git/R_project/Marketing_BS/Online Retail.xlsx",sheet="Online Retail")
df
```


```{r}
# ignore negative quantity
dim(df)
df <- df[which(df$Quantity > 0),]
dim(df)

# remove records with NA
df <- na.omit(df)
dim(df)

# excluding incomplete month
sprintf("Date Range: %s ~ %s", min(df$InvoiceDate), max(df$InvoiceDate))
dim(df)
df <- df[which(df$InvoiceDate < '2011-12-01'),]
dim(df)

# total sales
df$Sales <- df$Quantity * df$UnitPrice

# per customer data
customerDF <- df %>% 
  group_by(CustomerID) %>% 
  dplyr::summarize(TotalSales=sum(Sales), OrderCount=length(unique(InvoiceDate))) %>%
  mutate(AvgOrderValue=TotalSales/OrderCount)
customerDF
```

```{r}

# library(quantable)
# class(robustscale(customerDF["OrderCount"])) # list
# as.data.frame(robustscale(customerDF["OrderCount"]))["OrderCount"] 
# class(as.data.frame(robustscale(customerDF["OrderCount"]))) # dataframe
# rb_scale <- quantable::robustscale(customerDF[,2:4])
# class(rb_scale) # list
# rb_scale # cannot scale all feature to same scale -1 --> 1, cannot combine to dataframe due to list

```

```{r}
# try standard scale by prop.table
customerDF_matrix <- as.matrix(customerDF[,-1])
customerDF_matrix_prop <- prop.table(customerDF_matrix,margin=2)
summary(customerDF_matrix_prop)
```
```{r}
summary(customerDF_matrix)
```

```{r}
# rank will give all column with the same range (from 1 to 4298)
rankDF <- customerDF %>%
  mutate(TotalSales=rank(TotalSales), OrderCount=rank(OrderCount, ties.method="first"), AvgOrderValue=rank(AvgOrderValue))
rankDF

```
```{r}
# normalize these rank
normalizedDF <- rankDF %>%
  mutate(TotalSales=scale(TotalSales), OrderCount=scale(OrderCount), AvgOrderValue=scale(AvgOrderValue))
normalizedDF
```

```{r}
#check for normalization - mean of 0 & std of 1
summary(normalizedDF)
sapply(normalizedDF, sd)
```

# Kmeans
```{r}
cluster <- kmeans(normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")], 4)
# cluster centers
cluster$centers
```


```{r}
# cluster labels
normalizedDF$Cluster <- cluster$cluster
normalizedDF
```
```{r}
normalizedDF %>% group_by(Cluster) %>% summarise(Count=n())
```

# find best kmean
```{r}
data_kmean <- normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")]
rownames(data_kmean) <- normalizedDF$CustomerID
data_kmean
```

```{r}

# Setup for k-means loop 
km.out <- list()
sil.out <- list()
x <- vector()
y <- vector()
minClust <- 3      # Hypothesized minimum number of segments
maxClust <- 8      # Hypothesized maximum number of segments
# Compute k-means clustering over various clusters, k, from minClust to maxClust
for (centr in minClust:maxClust) {
        i <- centr-(minClust-1) # relevels start as 1, and increases with centr
        set.seed(11) # For reproducibility
        km.out[i] <- list(kmeans(data_kmean, centers = centr, nstart = 50))
        sil.out[i] <- list(silhouette(km.out[[i]][[1]], dist(data_kmean)))
        # Used for plotting silhouette average widths
        x[i] = centr  # value of k
        y[i] = summary(sil.out[[i]])[[4]]  # Silhouette average width
}
```


```{r}
ggplot(data = data.frame(x, y), aes(x, y)) + 
  geom_point(size=3) + 
  geom_line() +
  xlab("Number of Cluster Centers") +
  ylab("Silhouette Average Width") +
  ggtitle("Silhouette Average Width as Cluster Center Varies")
```


```{r}
# Get attributes of optimal k-means output
# maxSilRow <- which.max(y)          # Row number of max silhouette value
maxSilRow <- 2          # Row number of max silhouette value
optimalClusters <- x[maxSilRow]    # Number of clusters
km.out.best <- km.out[[maxSilRow]] # k-means output of best cluster
maxSilRow # 3
optimalClusters # 4
```


```{r}
customerDF$Cluster <- km.out.best$cluster
customerDF
```


```{r}
# count per cluster
customerDF %>% group_by(Cluster) %>% summarise(Count=n())
```
```{r}
# Cluster size
cluster$size
```

```{r}
# cluster centers
cluster$centers
```

```{r}
str(cluster)
```

# Visual cluster

```{r}
library(factoextra) # clustering algorithms & visualization
fviz_cluster(cluster, data = data_kmean)
```

```{r}
p1<-normalizedDF %>% 
  ggplot(aes(x=factor(Cluster),y=TotalSales,color=factor(Cluster)))+
  geom_boxplot()

p2<-normalizedDF %>% 
  ggplot(aes(x=factor(Cluster),y=OrderCount,color=factor(Cluster)))+
  geom_boxplot()

p3<-normalizedDF %>% 
  ggplot(aes(x=factor(Cluster),y=AvgOrderValue,color=factor(Cluster)))+
  geom_boxplot()
library(gridExtra)
grid.arrange(p1, p2, p3)
```

Let's take a closer look at this. The fourth cluster has the lowest numbers for all three
attributes. This suggests that the fourth cluster contains customers with the smallest
amount of sales, smallest number of orders, and lowest average per-order value. This group
of customers is one of low-value customers. On the other hand, the third cluster has the
highest numbers for all three attributes. The customers in the third cluster have the greatest
amount of sales, greatest number of orders, and highest average per-order value. So, these
customers in the third cluster purchase expensive items and give the business the highest
revenue. You would typically want to focus your marketing efforts on this segment of
customers, as it will result in the highest return.


The customers in the second cluster are interesting. They make purchases relatively
frequently, as they have a medium-to-high cluster center value for OrderCount, but their
average per-order value is low, as the cluster center for AvgOrderValue is low. These are
the customers who make frequent purchases of low-value items. So, it would be perfect to
market items with low per-item prices to this segment of customers. The customers in the
first cluster are also interesting. Their contributions to the revenue and number of orders
are medium to low, looking at the centers of this cluster. However, their average per-order
value is high. These are the customers who buy expensive items infrequently. Thus, it
would be perfect to market expensive items to this segment of customers.

```{r}
cluster$centers
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

