---
title: "Untitled"
output: html_document
---
# Handson marketing chap 10
#### 1. Load Data ####
```{r}
df <- read_excel(
  path="./Online Retail.xlsx", 
  sheet="Online Retail"
)
df
```

#### 2. Date Clean-Up ####
. Dropping canceled orders: We are going to drop records with negative
Quantity, using the following code
```{r}
# ignore negative quantity
dim(df)
df <- df[which(df$Quantity > 0),]
dim(df)
```
Dropping records with no CustomerID: There are 133,361 records with
no CustomerID and we are going to drop those records with the following code:

```{r}
# remove records with NA
df <- na.omit(df)
dim(df)
```

Excluding an incomplete month: As you might recall from previous chapters,
the data in the month of December, 2011, is incomplete. You can exclude this
data with the following code:
```{r}
# excluding incomplete month
sprintf("Date Range: %s ~ %s", min(df$InvoiceDate), max(df$InvoiceDate))
dim(df)
df <- df[which(df$InvoiceDate < '2011-12-01'),]
dim(df)
```
Computing total sales from the Quantity and UnitPrice columns: For our
analyses, we need the total sales value, so we are going to multiply the
Quantity and UnitPrice columns, to get the total sales, as shown in the
following code:

```{r}
# total sales
df$Sales <- df$Quantity * df$UnitPrice
```
 Per-customer data: In order to analyze customer segments, we need to transform
our data, so that each record represents the purchase history of individual
customers. Take a look at the following code:
```{r}
# per customer data
customerDF <- df %>% 
  group_by(CustomerID) %>% 
  dplyr::summarize(TotalSales=sum(Sales), OrderCount=length(unique(InvoiceDate))) %>%
  mutate(AvgOrderValue=TotalSales/OrderCount)
customerDF
```

Now, as you can see from this data, the TotalSales, OrderCount, and AvgOrderValue
columns, have different scales. TotalSales can take any values from 0 to 26,848,
while OrderCount takes values between 1 and 201. Clustering algorithms are highly
affected by the scales of the data, so we need to normalize this data to be on the same scale.
We are going to take two steps to normalize this data. First, we are going to rank the data,
so that the values of each column range from 1 to 4298, which is the total number of
records. Take a look at the following code:
```{r}
rankDF <- customerDF %>%
  mutate(TotalSales=rank(TotalSales), OrderCount=rank(OrderCount, ties.method="first"), AvgOrderValue=rank(AvgOrderValue))
rankDF
```

Next, we are going to normalize this data to center around the mean, and have a mean
of 0 and a standard deviation of 1, using the scale function in R. Take a look at the
following code:
```{r}
normalizedDF <- rankDF %>%
                mutate(TotalSales=scale(TotalSales), OrderCount=scale(OrderCount),
                AvgOrderValue=scale(AvgOrderValue))
normalizedDF
```


```{r}
# check for normalization - mean of 0 & std of 1
summary(normalizedDF)
```
You can see that the values are centered around at 0 and have a standard deviation of 1.
We are going to use this data for the following clustering analyses.

```{r}
sapply(normalizedDF, sd)
```
#### 3. Customer Segmentation via K-Means Clustering ####
The k-means clustering algorithm is a frequently used algorithm to draw insights on the
formations and separations within the data. In marketing, it is often used to build customer
segments and understand the behaviors of these different segments. Let's dive into building
clustering models in R.
```{r}
cluster <- kmeans(normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")], 4)
cluster
```

As you can see from this code, we are building a clustering model that splits the data into 4
segments. The first parameter of the kmeans function is for the data to be used for k-means
clustering and the second parameter is to define the desired number of clusters. In this
code, we are building 4 clusters, based on the TotalSales, OrderCount,
and AvgOrderValue values. The trained k-means clustering model object, cluster, stores
the labels and centers of the clusters in the cluster and centers variables of the model
object. You can retrieve these values, as shown in the following code:
```{r}
# cluster centers
cluster$cluster
cluster$centers
```

Now that we have built our first clustering model, let's visualize this data. First, we are
going to store the cluster labels as a separate column, named Cluster, in the
normalizedDF variable, as shown in the following
```{r}
# cluster labels
normalizedDF$Cluster <- cluster$cluster
normalizedDF
```


```{r}
normalizedDF %>% group_by(Cluster) %>% summarise(Count=n())
```

Then, we can visualize the clusters, using the following code:
```{r}
ggplot(normalizedDF, aes(x=AvgOrderValue, y=OrderCount, color=Cluster)) +
  geom_point()
```
Let's take a closer look at this plot. The cluster in the bottom left is the group of low-value
customers, who have not purchased our products so much. On the other hand, the cluster
in the top right with the darkest color is the group of high-value customers, who have
purchased the greatest amount and who have purchased products frequently. We can also
visualize the clusters with different angles, using the rest of the variables. Take a look at the
following plots:

```{r}
ggplot(normalizedDF, aes(x=TotalSales, y=OrderCount, color=Cluster)) +
  geom_point()
```


```{r}
ggplot(normalizedDF, aes(x=TotalSales, y=AvgOrderValue, color=Cluster)) +
  geom_point()
```
The first plot shows the clusters visualized based on AvgOrderValue and OrderCount. On
the other hand, the second plot the clusters visualized based on
AvgOrderValue and TotalSales. As you can see from these plots, the cluster in the
bottom left with the second-lightest color has the lowest average per-order value and the
lowest number of orders. However, the cluster in the top right with the darkest color has
the highest average per-order value and the greatest number of orders. Visualizing clusters
helps you understand the characteristics of different clusters much more easily and clearly.

```{r}
# Selecting the best number of cluster
library(cluster)
```


```{r}
for(n_cluster in 4:8){
  cluster <- kmeans(normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")], n_cluster)
  
  silhouetteScore <- mean(
    silhouette(
      cluster$cluster, 
      dist(normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")], method = "euclidean")
    )[,3]
  )
  print(sprintf('Silhouette Score for %i Clusters: %0.4f', n_cluster, silhouetteScore))
}
```
In our case, of the five different numbers of clusters we have experimented with, the best
number of clusters with the highest silhouette score was 4. In the following section, we will
use 4 for the number of clusters to show how we can interpret the results of clustering
analysis.

```{r}
# Interpreting customer segments
cluster <- kmeans(normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")], 4)
normalizedDF$Cluster <- cluster$cluster
```

```{r}
# count per cluster
normalizedDF %>% group_by(Cluster) %>% summarise(Count=n())
```


```{r}
# cluster centers
cluster$centers
```
Let's take a closer look at this. The third cluster has the lowest numbers for all three
attributes. This suggests that the third cluster contains customers with the lowest amount of
sales, lowest number of orders, and lowest average per-order value. This group of
customers is a group of low-value customers. On the other hand, the fourth cluster has the
highest numbers for all three attributes. The customers in the fourth cluster have the
highest amount of sales, highest number of orders, and highest average per-order value.
This suggests that these customers in the fourth cluster purchase expensive items and give
the business the highest revenue. You would typically want to focus your marketing efforts
on this segment of customers, as it will result in the highest return.

The customers in the first cluster are interesting. They make purchases relatively
frequently, as they have a medium to high cluster center value for OrderCount, but their
average per-order value is low, as the cluster center for AvgOrderValue is low. These are
the type of customers who make frequent purchases of low-value items. So, it would be
perfect to market items with low per-item prices to this segment of customers. The
customers in the second cluster are also interesting. Their contributions to the revenue and
number of orders are low, looking at the centers of this cluster. However, their average perorder value is high. These are the type of customers who buy expensive items infrequently.
Thus, it would be perfect to market expensive items to this segment of customers.
```{r}
# High value cluster summary
summary(customerDF[which(normalizedDF$Cluster == 4),])
```

As you can see from this example, looking at the centers of clusters helps us understand
different types and segments of customers and how to target them differently. Lastly, we
can also find out what the best-selling items are for each customer segment. Take a look at
the following code:
```{r}
highValueCustomers <- unlist(
  customerDF[which(normalizedDF$Cluster == 4),'CustomerID'][,1], use.names = FALSE
)
#highValueCustomers
```


```{r}
df[which(df$CustomerID %in% highValueCustomers),] %>%
  group_by(Description) %>%
  summarise(Count=n()) %>%
  arrange(desc(Count))
```
As we have seen before, the fourth cluster was the group of high-value customers and we
are going to take a look at the best-selling items for this group. The output of this code is
shown in the following screenshot:
For this high-value segment, the best-selling item was JUMBO BAG RED
RETROSPOT and the second best-selling item was REGENCY CAKESTAND 3 TIER. You
can utilize this information in the marketing strategies, when you target this customer
segment. In your marketing campaigns, you can recommend items similar to these bestselling items to this segment of customers, as they are the most interested in these types of
items.

#2 Customer segment by DNN
```{r}
library(readxl)
library(tidyverse)
```

```{r}
df <- read_excel(path="./Online Retail.xlsx",sheet="Online Retail")
df
```


```{r}
# ignore negative quantity
dim(df)
df <- df[which(df$Quantity > 0),]
dim(df)

# remove records with NA
df <- na.omit(df)
dim(df)

# excluding incomplete month
sprintf("Date Range: %s ~ %s", min(df$InvoiceDate), max(df$InvoiceDate))
dim(df)
df <- df[which(df$InvoiceDate < '2011-12-01'),]
dim(df)

# total sales
df$Sales <- df$Quantity * df$UnitPrice

# per customer data
customerDF <- df %>% 
  group_by(CustomerID) %>% 
  dplyr::summarize(TotalSales=sum(Sales), OrderCount=length(unique(InvoiceDate))) %>%
  mutate(AvgOrderValue=TotalSales/OrderCount)
customerDF
```

```{r}

# library(quantable)
# class(robustscale(customerDF["OrderCount"])) # list
# as.data.frame(robustscale(customerDF["OrderCount"]))["OrderCount"] 
# class(as.data.frame(robustscale(customerDF["OrderCount"]))) # dataframe
# rb_scale <- quantable::robustscale(customerDF[,2:4])
# class(rb_scale) # list
# rb_scale # cannot scale all feature to same scale -1 --> 1, cannot combine to dataframe due to list

```
```{r}
# try standard scale by prop.table
customerDF_matrix <- as.matrix(customerDF[,-1])
customerDF_matrix_prop <- prop.table(customerDF_matrix,margin=2)
summary(customerDF_matrix_prop)
```
```{r}
summary(customerDF_matrix)
```

```{r}
# rank will give all column with the same range (from 1 to 4298)
rankDF <- customerDF %>%
  mutate(TotalSales=rank(TotalSales), OrderCount=rank(OrderCount, ties.method="first"), AvgOrderValue=rank(AvgOrderValue))
rankDF

```
```{r}
# normalize these rank
normalizedDF <- rankDF %>%
  mutate(TotalSales=scale(TotalSales), OrderCount=scale(OrderCount), AvgOrderValue=scale(AvgOrderValue))
normalizedDF
```

```{r}
#check for normalization - mean of 0 & std of 1
summary(normalizedDF)
sapply(normalizedDF, sd)
```

# Kmeans
```{r}
cluster <- kmeans(normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")], 4)
# cluster centers
cluster$centers
```


```{r}
# cluster labels
normalizedDF$Cluster <- cluster$cluster
normalizedDF
```
```{r}
normalizedDF %>% group_by(Cluster) %>% summarise(Count=n())
```

# find best kmean
```{r}
data_kmean <- normalizedDF[c("TotalSales", "OrderCount", "AvgOrderValue")]
rownames(data_kmean) <- normalizedDF$CustomerID
data_kmean
```

```{r}

# Setup for k-means loop 
km.out <- list()
sil.out <- list()
x <- vector()
y <- vector()
minClust <- 2      # Hypothesized minimum number of segments
maxClust <- 8      # Hypothesized maximum number of segments
# Compute k-means clustering over various clusters, k, from minClust to maxClust
for (centr in minClust:maxClust) {
        i <- centr-(minClust-1) # relevels start as 1, and increases with centr
        set.seed(11) # For reproducibility
        km.out[i] <- list(kmeans(data_kmean, centers = centr, nstart = 50))
        sil.out[i] <- list(silhouette(km.out[[i]][[1]], dist(data_kmean)))
        # Used for plotting silhouette average widths
        x[i] = centr  # value of k
        y[i] = summary(sil.out[[i]])[[4]]  # Silhouette average width
}
```


```{r}
ggplot(data = data.frame(x, y), aes(x, y)) + 
  geom_point(size=3) + 
  geom_line() +
  xlab("Number of Cluster Centers") +
  ylab("Silhouette Average Width") +
  ggtitle("Silhouette Average Width as Cluster Center Varies")
```


```{r}
# Get attributes of optimal k-means output
# maxSilRow <- which.max(y)          # Row number of max silhouette value
maxSilRow <- 3          # Row number of max silhouette value
optimalClusters <- x[maxSilRow]    # Number of clusters
km.out.best <- km.out[[maxSilRow]] # k-means output of best cluster
maxSilRow # 3
optimalClusters # 4
```


```{r}
customerDF$Cluster <- km.out.best$cluster
customerDF
```


```{r}
# count per cluster
customerDF %>% group_by(Cluster) %>% summarise(Count=n())
```
```{r}
# Cluster size
cluster$size
```


```{r}
# cluster centers
cluster$centers
```

Let's take a closer look at this. The third cluster has the lowest numbers for all three
attributes. This suggests that the third cluster contains customers with the lowest amount of
sales, lowest number of orders, and lowest average per-order value. This group of
customers is a group of low-value customers. On the other hand, the fourth cluster has the
highest numbers for all three attributes. The customers in the fourth cluster have the
highest amount of sales, highest number of orders, and highest average per-order value.
This suggests that these customers in the fourth cluster purchase expensive items and give
the business the highest revenue. You would typically want to focus your marketing efforts
on this segment of customers, as it will result in the highest return.

```{r}
str(cluster)
```

# Visual cluster

```{r}
library(factoextra) # clustering algorithms & visualization
fviz_cluster(cluster, data = data_kmean)
```


```{r}
k2 <- kmeans(data_kmean, centers = 2, nstart = 25)
k3 <- kmeans(data_kmean, centers = 3, nstart = 25)
k4 <- kmeans(data_kmean, centers = 4, nstart = 25)
k5 <- kmeans(data_kmean, centers = 5, nstart = 25)

# plots to compare
p1 <- fviz_cluster(k2, geom = "point", data = data_kmean) + ggtitle("k = 2")
p2 <- fviz_cluster(k3, geom = "point",  data = data_kmean) + ggtitle("k = 3")
p3 <- fviz_cluster(k4, geom = "point",  data = data_kmean) + ggtitle("k = 4")
p4 <- fviz_cluster(k5, geom = "point",  data = data_kmean) + ggtitle("k = 5")

library(gridExtra)
grid.arrange(p1, p2, p3, p4, nrow = 2)
```

```{r}
# Cannot see sth in this plot due to outlier
customerDF %>% 
  ggplot(aes(x=factor(Cluster),y=TotalSales))+
   geom_boxplot()
```

```{r}
p1<-normalizedDF %>% 
  ggplot(aes(x=factor(Cluster),y=TotalSales,color=factor(Cluster)))+
  geom_boxplot()

p2<-normalizedDF %>% 
  ggplot(aes(x=factor(Cluster),y=OrderCount,color=factor(Cluster)))+
  geom_boxplot()

p3<-normalizedDF %>% 
  ggplot(aes(x=factor(Cluster),y=AvgOrderValue,color=factor(Cluster)))+
  geom_boxplot()
library(gridExtra)
grid.arrange(p1, p2, p3)
```
```{r}
cluster$centers
```

# PCA
```{r}
res.pca <- prcomp(data_kmean)
res.pca
```

```{r}
summary(res.pca)
```


```{r}
library(plotly)
ggplotly(fviz_eig(res.pca))
```


```{r}
fviz_pca_ind(res.pca,
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )
```
```{r}
pca$rotation
```

```{r}
pca4.dat <- cbind(pca, group=k4$cluster)
pca4.dat
```



```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

